### 2017-04-16 proposal.tex
Boilerplate

% Template from Usenix
\documentclass[letterpaper,twocolumn,10pt]{article}
\usepackage{usenix,epsfig,endnotes}
\begin{document}

% Don't output date
\date{}

% Title
\title{\Large \textbf{
(TODO: Project Name) - Project Proposal } \\ \vspace{0.025 in} \large \normalfont
CSE 227: Computer Security - Spring 2017 \\ \textit{
University of California San Diego
}}

% Authors
\author{
{\rm Chen Lai}\\
\normalfont{\texttt{chl588@ucsd.edu}}
\and
{\rm Zhongrong Jian}\\
\normalfont{\texttt{zhjian@ucsd.edu}}
\and
{\rm Juan Sidrach}\\
\normalfont{\texttt{jsidrach@ucsd.edu}}
}

\maketitle

\section{Introduction}
TODO

\section{Section}
TODO~\cite{ipv4sta}

{\footnotesize \bibliographystyle{acm}
\bibliography{bibliography}}

\end{document}

### 2017-04-27 proposal.tex
Topic selected + Proposal structure

@@
 \usepackage{usenix,epsfig,endnotes}
+\usepackage{graphicx}
+
 \begin{document}
@@
 \title{\Large \textbf{
-(TODO: Project Name) - Project Proposal } \\ \vspace{0.025 in} \large \normalfont
+\includegraphics[height=\baselineskip]{title} \\
+Project Proposal } \\ \vspace{0.025 in} \large \normalfont
 CSE 227: Computer Security - Spring 2017 \\ \textit{
@@
 
-\section{Introduction}
-TODO
+\section{What}
+- Explain the attack
+  - When/how were IDN introduced
+  - Homograph letters
+  - How to use this to the attackers advantage
 
-\section{Section}
-TODO~\cite{ipv4sta}
+- Research
+  - On websites
+    - Top 500 Alexa Websites
+    - Try all possible variations
+    - Classify: 404, redirect (legitimate), malicious, unrelated
+    - Evaluation
+  - On browsers
+    - % Affected, version affected
+    - Screenshots before/after CVE (url bar, hover link)
+    - Other possible policies: why they may work or they won't
+      - Maybe domain providers should not allow IDNs close to real names?
+      - Whitelist/blacklist
 
-{\footnotesize \bibliographystyle{acm}
-\bibliography{bibliography}}
+- Conclusion
+  - Impact of the vulnerability based on empirical data and % of users still vulnerable
+
+\section{Why}
+- Relatively new CVE discovered because this (https://bugs.chromium.org/p/chromium/issues/detail?id=683314)
+- How something beneficial for the users IDN could be turned against them
+- Hard for regular users to distinguish between real/fake sites
+- Easy to collect data to evaluate impact
+
+\section{Potential Issues}
+- The potential impact, it may be actually really low
+- If we will find not legitimate sites by substitution (sample size may be low)
+- If there are a lot of illegitime sites, we would need to check manually if they are just a redirect or a scam, maybe we will need to find an automatic way
+
+\section{Resources}
+Resources
+- We believe for the TOP500 sites + variations of each one we can check it with our own computers/crawlers, same for different browsers
 

### 2017-04-27 proposal.tex
finish explain the attack

@@
 \section{What}
+
 - Explain the attack
@@
   - How to use this to the attackers advantage
+
+Domain name were designed to support ASCII character.
+Internationalized domain name(IDN) was proposed in December 1996 by Martin Dürst for the purpose of letting non-English speaking people use Internet without restriction[1].
+The solution is to implement unicode mapping every character in different language to a unique number.
+Homograph letters, however, could be a potential vulnerability.
+For example, Cyrillic letter 'a' can look identical to Latin letter 'a'.
+Attackers can use the website "www.apple.com" where 'a' actually is a Cyrillic letter to attack users.
+In some other language, like Chinese, there exists many homographs between traditional Chinese and simplified Chinese.
 
@@
   - Impact of the vulnerability based on empirical data and % of users still vulnerable
+  - Possible solution for this vulnerability. How does company solve this problem.
 

### 2017-04-27 proposal.tex
Update proposal

@@
 
+In terms of URL variations, We will mainly focus our research on Top 500 Alexa websites, replacing the domain name with all possible variations.
+By checking the status code of return pages, we can classify the websites into different categories: page not found(404), redirection to legitimate url, malicious variations and unrelated variations.
+We will evaluate the impact of this vulnerability based on the percentage of malicious variations of the websites and potential impact based on the percentage of pages with 404.
+On the other hand, browser plays an important role in defending against IDN homograph attack.
+In this project, the exposure to this vulnerability of different versions of the major browsers will be studied.
+We will discuss about the solutions given by these companies and how effective those solutions are along with some screenshots of them before and after the CVE is disclosed.
+In addition, we will also take a look at some other policies, for example, whitelist and blacklist, and analyze the possible disadvantages.
+
 - Conclusion
@@
   - Possible solution for this vulnerability. How does company solve this problem.
+
+At the end of this project, we will have an evaluation of the current impact of the vulnerability based on the empirical data so that we can have an idea of the potential impact and the percentage of users involved.
 
@@
 
+This CVE was recently disclosed and few relevant researches have been done.
+It's interesting to find how internationalized domain name which was designed to be beneficial is utilized by malicious user and turn against regular users' back.
+It's also fairly difficult for regular users to distinguish between legitimate websites and the variant ones so we are hoping to find out how browser protect regular users from this vulnerability after its disclosure.
+Moreover, the impact of this CVE can be evaluated statistically and it is easy to collect data.
+
 \section{Potential Issues}
@@
 - If there are a lot of illegitime sites, we would need to check manually if they are just a redirect or a scam, maybe we will need to find an automatic way
+
+There are some potential issues and limitations on this project.
+The potential or the real impact could be actually negligible.
+Since we are only collecting data from top 500 Alexa websites which makes the sample size so small that we may find very few legitimate sites by substitution.
+Additionally, we would need to check manually the categories the illegitimate websites belongs to till we find a way to automatize the process.
 

### 2017-04-27 docs/paper.tex
Proposal, reorganize structure

--- 2017-04-27 proposal.tex
@@
-% Template from Usenix
 \documentclass[letterpaper,twocolumn,10pt]{article}
 \usepackage{usenix,epsfig,endnotes}
-\usepackage{graphicx}
-
 \begin{document}
@@
 % Title
-\title{\Large \textbf{
-\includegraphics[height=\baselineskip]{title} \\
-Project Proposal } \\ \vspace{0.025 in} \large \normalfont
+\title{\Large
+\includegraphics[height=\baselineskip]{title}
+\\ \vspace{0.025 in} \large \normalfont
 CSE 227: Computer Security - Spring 2017 \\ \textit{
@@
 \and
-{\rm Juan Sidrach}\\
+{\rm J. Sidrach}\\
 \normalfont{\texttt{jsidrach@ucsd.edu}}
@@
 
-\section{What}
-- Explain the attack
-  - When/how were IDN introduced
-  - Homograph letters
-  - How to use this to the attackers advantage
+\abstract{TODO}
 
-- Research
-  - On websites
-    - Top 500 Alexa Websites
-    - Try all possible variations
-    - Classify: 404, redirect (legitimate), malicious, unrelated
-    - Evaluation
-  - On browsers
-    - % Affected, version affected
-    - Screenshots before/after CVE (url bar, hover link)
-    - Other possible policies: why they may work or they won't
-      - Maybe domain providers should not allow IDNs close to real names?
-      - Whitelist/blacklist
+\section{Introduction}
+TODO
 
-- Conclusion
-  - Impact of the vulnerability based on empirical data and % of users still vulnerable
+\section{Section}
+TODO
 
-\section{Why}
-- Relatively new CVE discovered because this (https://bugs.chromium.org/p/chromium/issues/detail?id=683314)
-- How something beneficial for the users IDN could be turned against them
-- Hard for regular users to distinguish between real/fake sites
-- Easy to collect data to evaluate impact
+\section{Availability}
+TODO~\cite{ipv4sta}\endnote{Endnote}
 
-\section{Potential Issues}
-- The potential impact, it may be actually really low
-- If we will find not legitimate sites by substitution (sample size may be low)
-- If there are a lot of illegitime sites, we would need to check manually if they are just a redirect or a scam, maybe we will need to find an automatic way
+{\footnotesize \bibliographystyle{acm}
+\bibliography{bibliography}}
 
-\section{Resources}
-Resources
-- We believe for the TOP500 sites + variations of each one we can check it with our own computers/crawlers, same for different browsers
+\theendnotes
 

### 2017-04-27 docs/proposal.tex
Proposal, reorganize structure

\documentclass[letterpaper,twocolumn,10pt]{article}
\usepackage{usenix,epsfig,endnotes}
\usepackage{graphicx}

\begin{document}

% Don't output date
\date{}

% Title
\title{\Large \textbf{
\includegraphics[height=\baselineskip]{title} \\
Project Proposal } \\ \vspace{0.025 in} \large \normalfont
CSE 227: Computer Security - Spring 2017 \\ \textit{
University of California San Diego
}}

% Authors
\author{
{\rm Chen Lai}\\
\normalfont{\texttt{chl588@ucsd.edu}}
\and
{\rm Zhongrong Jian}\\
\normalfont{\texttt{zhjian@ucsd.edu}}
\and
{\rm J. Sidrach}\\
\normalfont{\texttt{jsidrach@ucsd.edu}}
}

\maketitle

\section{What}

Domain names were originally designed to support only ASCII characters.
Internationalized Domain Names (IDN) were proposed back in December 1996 by Martin Dürst for the purpose of letting non-English speaking people use Internet without  additional restriction.
This extension involves representing Unicode characters in ASCII using Punycode, so that they could be then rendered back into their Unicode representation.
Homograph letters (different letters whose representation is almost, if not, the same), however, present a potential vulnerability.
For example, Cyrillic letter 'a' can look identical to Latin letter 'a' depending on the font.
In other languages, like Chinese, there exists many homograph letters between traditional Chinese and simplified Chinese.
Malicious attackers can then register a domain where one of the letters is actually Cyrillic but whose representation matches a Latin one.
Users could be linked to this newly registered malicious page, and they may not have any visual indication (at least without further interaction) that the page is not the one they think they are visiting.

\section{How}
We will focus our research on the Top 500 Alexa websites, specifically in URL variations where Latin characters are replaced by Cyrillic ones with a similar representation.
By checking and verifying the domain variations, we will classify them into different categories: not registered, owned by the same entity as the original, malicious and unrelated.
We will evaluate the impact of this vulnerability based on the relative percentages we find in the different categories.

On the other hand, browsers also play an important role in defending against IDN homograph attacks.
In this project, the exposure to this vulnerability of different versions of the major browsers will be studied.
We will discuss the solutions given by these browsers and their effectiveness, along with some screenshots of the browser's navigation bar before and after related CVEs were disclosed.
Finally, we will also explore alternative policies, for instance, white/black lists and unconditional rendering, to analyze the possible advantages and drawbacks of each one.

At the end of this project, we will have a statistical evaluation of the current impact of this kind of vulnerability based on the empirical data, so that we can have an idea of the potential impact and the percentage of users at risk.

\section{Potential Issues}
Since we are only collecting data from the Top 500 Alexa websites, the sample size may be too small to find enough illegitimate domain names by just substituting characters by visually equivalent Unicode homoglyphs.
Second, we will need to manually check and classify the illegitimate websites.
This could be a significant time investment if the amount of registered domain names we find by character substitution is high, unless we find a suitable solution to automate the process.

\section{Resources}
We believe that we can perform the empirical study in our own computers, as we will limit the search to the Top 500 Alexa websites.
We also think that we can test different browsers/environments without additional resources.

\end{document}

### 2017-04-28 docs/proposal.tex
Fix typos

@@
 Domain names were originally designed to support only ASCII characters.
-Internationalized Domain Names (IDN) were proposed back in December 1996 by Martin Dürst for the purpose of letting non-English speaking people use Internet without  additional restriction.
+Internationalized Domain Name (IDN) was proposed back in December 1996 by Martin Dürst for the purpose of letting non-English speaking people use Internet without  additional restrictions.
 This extension involves representing Unicode characters in ASCII using Punycode, so that they could be then rendered back into their Unicode representation.
@@
 In this project, the exposure to this vulnerability of different versions of the major browsers will be studied.
-We will discuss the solutions given by these browsers and their effectiveness, along with some screenshots of the browser's navigation bar before and after related CVEs were disclosed.
-Finally, we will also explore alternative policies, for instance, white/black lists and unconditional rendering, to analyze the possible advantages and drawbacks of each one.
+We will discuss the solutions implemented by these browsers and their effectiveness, along with some screenshots of the browsers' navigation bar before and after related CVEs were disclosed.
+Finally, we will also explore alternative policies, as white/black lists and unconditional rendering, and analyze the possible advantages and drawbacks of each one.
 
@@
 Since we are only collecting data from the Top 500 Alexa websites, the sample size may be too small to find enough illegitimate domain names by just substituting characters by visually equivalent Unicode homoglyphs.
-Second, we will need to manually check and classify the illegitimate websites.
+Second, we may need to manually check and classify the illegitimate websites.
 This could be a significant time investment if the amount of registered domain names we find by character substitution is high, unless we find a suitable solution to automate the process.

### 2017-05-01 src/confusables_map.go
Homographs detection code

@@ -1,0 +1,6185 @@
+// DO NOT EDIT - Autogenerated file with generate_confusables.go
+
+package homographs
+
+// Original header of the source confusables file:
+// confusables.txt
+// Date: 2016-06-16, 13:41:30 GMT
+// © 2016 Unicode®, Inc.
+// Unicode and the Unicode Logo are registered trademarks of Unicode, Inc. in the U.S. and other countries.
+// For terms of use, see http://www.unicode.org/terms_of_use.html
+//
+// Unicode Security Mechanisms for UTR #39
+// Version: 9.0.0
+//
+// For documentation and usage, see http://www.unicode.org/reports/tr39
+//
+
+var confusablesMap = map[rune]string{
+	0x000005AE: "\u0598",
+	0x000005A8: "\u0599",
+	0x000005A4: "\u059a",
+	0x00001AB4: "\u06db",
+	0x000020DB: "\u06db",
+	0x00000619: "\u0313",
+	0x000008F3: "\u0313",
+	0x00000343: "\u0313",
+	0x00000315: "\u0313",
+	0x0000064F: "\u0313",
+	0x0000065D: "\u0314",
+	0x0000059C: "\u0301",
+	0x0000059D: "\u0301",
+	0x00000618: "\u0301",
+	0x00000747: "\u0301",
+	0x00000341: "\u0301",
+	0x00000954: "\u0301",
+	0x0000064E: "\u0301",
+	0x00000340: "\u0300",
+	0x00000953: "\u0300",
+	0x0000030C: "\u0306",
+	0x0000A67C: "\u0306",
+	0x00000658: "\u0306",
+	0x0000065A: "\u0306",
+	0x0000036E: "\u0306",
+	0x000006E8: "\u0306\u0307",
+	0x00000310: "\u0306\u0307",
+	0x00000901: "\u0306\u0307",
+	0x00000981: "\u0306\u0307",
+	0x00000A81: "\u0306\u0307",
+	0x00000B01: "\u0306\u0307",
+	0x00000C00: "\u0306\u0307",
[…]

### 2017-05-01 src/generate_confusables.go

@@ -1,0 +1,167 @@
+// +build ignore
+
+// Confusables dictionary generator
+// See http://www.unicode.org/reports/tr39/
+
+package main
+
+import (
+	"bufio"
+	"bytes"
+	"fmt"
+	"go/format"
+	"log"
+	"os"
+	"strconv"
+	"strings"
+)
+
+func main() {
+	parseConfusables()
+	writeConfusablesMap()
+}
+
+const (
+	// Confusables file
+	// 	Format:
+	// 		05AD ;	0596 ;	MA	# ( ֭ → ֖ ) HEBREW ACCENT DEHI → HEBREW ACCENT TIPEHA	#
+	// 	See http://www.unicode.org/reports/tr39/ for full explanation
+	ConfusablesFile = "../data/confusables.txt"
+	// Output package name
+	PackageName = "homographs"
+	// Generated output file
+	OutputFile = "confusables_map.go"
+)
+
+const (
+	// Fields of each line
+	CSourceCodePoint = iota
+	CTargetCodePoint
+	CType
+	NumField
+)
+
+// Type C encapsulates a line of the confusables file
+// 	(Character -> Skeleton Character(s))
+type C struct {
+	k rune
+	v []rune
+}
+
+// Generated file header
+var header []byte
+
+// Array of confusables (Character -> Skeleton Character)
+var confusables []C
+
+// Parse unicode confusables
+// 	Fills the header and confusable arrays
+func parseConfusables() {
+	// Open file
+	f, err := os.Open(ConfusablesFile)
+	if err != nil {
+		log.Fatal(err)
+	}
+	defer f.Close()
+	scanner := bufio.NewScanner(f)
+	// Parse header
+	header = []byte("// Original header of the source confusables file:\n")
+	for scanner.Scan() {
+		if parseHeader(scanner.Text()) {
+			break
+		}
+	}
+	// Parse confusables
+	for scanner.Scan() {
+		parseLine(scanner.Text())
+	}
+	if scanner.Err() != nil {
+		log.Fatal(scanner.Err())
+	}
+}
+
+// Writes the confusables map (as a go source file)
+func writeConfusablesMap() {
+	out := "// DO NOT EDIT - File autogenerated with generate_confusables.go\n\n"
+	out += "package " + PackageName + "\n\n"
+	// Header
+	out += fmt.Sprintf("%s\n", header)
+	// Confusables
+	out += fmt.Sprint("var confusablesMap = map[rune]string{\n")
+	for _, c := range confusables {
[…]

### 2017-05-01 src/homographs.go

@@ -1,0 +1,35 @@
+// go:generate go run generate_confusables.go
+
+package homographs
+
+import (
+	"unicode/utf8"
+
+	"golang.org/x/text/unicode/norm"
+)
+
+// Skeleton converts a string to it's "skeleton" form
+// 	See http://www.unicode.org/reports/tr39/#Confusable_Detection
+func Skeleton(s string) string {
+	// Convert s to NFD format
+	s = norm.NFD.String(s)
+	// Successively map each source character in s to the target string
+	for i, w := 0, 0; i < len(s); i += w {
+		char, width := utf8.DecodeRuneInString(s[i:])
+		// Use the confusables generated map
+		replacement, exists := confusablesMap[char]
+		if exists {
+			s = s[:i] + replacement + s[i+width:]
+			w = len(replacement)
+		} else {
+			w = width
+		}
+	}
+	// Reapply NFD
+	return norm.NFD.String(s)
+}
+
+// Returns true if two strings have the same skeleton (could be confused)
+func Confusable(x, y string) bool {
+	return Skeleton(x) == Skeleton(y)
+}

### 2017-06-06 docs/paper.tex
Paper outline

@@
 TODO
+- Introduction to the problem
+- Enumeration of sections this paper talks about
 
-\section{Section}
+\section{Background}
 TODO
+- DNS: explanation
+- IDN: history, explanation
+- Browsers: display of IDNs, algorithms
 
-\section{Availability}
+\section{Related Work}
+TODO
+- Brief analysis of previous papers on the same topic
+
+\section{Methodology}
+TODO
+- Introduction to the methodology
+- Subsection: data collection
+- Subsection: data pre-processing
+- Subsection: clustering, confusables algorithm
+- Subsection: manual classification, guidelines used
+
+\section{Results}
+TODO
+- Different results obtained
+
+\section{Ethical Considerations}
+TODO
+- Brief explanation why this research is ethical
+
+\section{Conclusions}
+TODO
+- Conclusions of our work
+- Possible future work
+
+\section*{Acknowledgements}
+- Thank prof/TA
 TODO~\cite{ipv4sta}\endnote{Endnote}

### 2017-06-08 docs/paper.tex
Add tables and acknowledgements

@@
 \documentclass[letterpaper,twocolumn,10pt]{article}
-\usepackage{usenix,epsfig,endnotes}
+\usepackage{epsfig,endnotes}
 \begin{document}
@@
 - Introduction to the methodology
+  - Reference github repository
 - Subsection: data collection
+  - Reference sources of data
 - Subsection: data pre-processing
 - Subsection: clustering, confusables algorithm
+  - Caveats: not mathing /, .com, etc.
 - Subsection: manual classification, guidelines used
@@
 TODO
-- Different results obtained
+- Comment different results obtained
+- Explain consequences of caveats (low number of matches)
+- Explain tables
+- Some other interesting results (topic-related domain hoarding)
+
+\begin{table}[]
+\centering
+\begin{tabular}{|l|r|r|}
+\hline
+\bfseries\sffamily{Domains}                   & \bfseries\sffamily{\#}     & \bfseries\sffamily{\%}     \\ \hline
+\itshape\sffamily{Canonical domain names}     & \itshape\sffamily{458731}  & \itshape\sffamily{8.31\%}  \\ \hline
+\hspace{0.5cm} With IDN homographs            & 825                        & 6.04\%                     \\ \hline
+\hspace{0.5cm} Without IDN homograpphs        & 457906                     & 2.27\%                     \\ \hline
+\itshape\sffamily{International Domain Names} & \itshape\sffamily{1045400} & \itshape\sffamily{91.69\%} \\ \hline
+\hspace{0.5cm} With canonical homograph       & 1099                       & 3.68\%                     \\ \hline
+\hspace{0.5cm} Without canonical homograph    & 1044301                    & 2.74\%                     \\ \hline
+\end{tabular}
+\caption{Overview of the clustering results.}
+\label{clustering-results}
+\end{table}
+
+\begin{table}[]
+\centering
+\begin{tabular}{|l|r|}
+\hline
+\bfseries\sffamily{Domain} & \bfseries\sffamily{\# of IDN homographs} \\ \hline
+google.com                 & 24                                       \\ \hline
+youtube.com                & 3                                        \\ \hline
+facebook.com               & 9                                        \\ \hline
+baidu.com                  & 3                                        \\ \hline
+yahoo.com                  & 4                                        \\ \hline
+reddit.com                 & 1                                        \\ \hline
+qq.com                     & 2                                        \\ \hline
+taobao.com                 & 1                                        \\ \hline
+live.com                   & 1                                        \\ \hline
+vk.com                     & 6                                        \\ \hline
+\end{tabular}
+\caption{Top ten .com domains in the Alexa ranking with IDN homographs.}
+\label{top-com-alexa-with-idns}
+\end{table}
+
+\begin{table}[]
+\centering
+\begin{tabular}{|l|r|r|}
+\hline
+\bfseries\sffamily{Status}           & \bfseries\sffamily{\#} & \bfseries\sffamily{\%}     \\ \hline
+\itshape\sffamily{Canonical}         & \itshape\sffamily{88}  & \itshape\sffamily{8.31\%}  \\ \hline
+\hspace{0.5cm} Parking               & 64                     & 6.04\%                     \\ \hline
+\hspace{0.5cm} Redirect              & 24                     & 2.27\%                     \\ \hline
+\itshape\sffamily{Third Party}       & \itshape\sffamily{971} & \itshape\sffamily{91.69\%} \\ \hline
+\hspace{0.5cm} Redirect to Canonical & 39                     & 3.68\%                     \\ \hline
+\hspace{0.5cm} Unrelated             & 29                     & 2.74\%                     \\ \hline
+\hspace{0.5cm} Parking               & 872                    & 82.34\%                    \\ \hline
+\hspace{0.5cm} Scam                  & 31                     & 2.93\%                     \\ \hline
+\end{tabular}
+\caption{Breakdown of the manually classified homograph IDNs.}
+\label{manually-classified-idns}
+\end{table}
+
+TODO: mention:
+  Number of Third Party domains whose Registrant Organization and Email has than one homograph IDN registered: 437
+  Number of Registrant's Organization and Email that have more than one homograph IDN: 82
+
+\begin{table*}[]
+\centering
+\begin{tabular}{|l|l|r|}
+\hline
+\bfseries\sffamily{Registrant organization} & \bfseries\sffamily{Registrant email} & \bfseries\sffamily{\# of homograph IDNs} \\ \hline
+Domains By Proxy, LLC                & --                         & 89                                                        \\ \hline
+Super Privacy Service c/o Dynadot    & privacy@dynadot.com        & 23                                                        \\ \hline
+Domain Registries Foundation         & --                         & 22                                                        \\ \hline
+Duong Thien                          & thiendv@outlook.com        & 18                                                        \\ \hline
+Syngenuity Limited                   & manager@syngenuity.com     & 12                                                        \\ \hline
+Helpnet: Brand Development \& Sales  & help@strongestbrands.com   & 12                                                        \\ \hline
+ONUNO L.L.C.                         & corucas@gmail.com          & 11                                                        \\ \hline
+Privacy Protection Service INC d/b/a & contact@privacyprotect.org & 10                                                        \\ \hline
+Hubertus Henz                        & hu\_h5@yahoo.de            & 9                                                         \\ \hline
+wuyu                                 & wy65535@126.com            & 7                                                         \\ \hline
+\end{tabular}
+\caption{Top ten registrants with the most homograph IDNs.}
+\label{top-registrants-homograph-idns}
+\end{table*}
 
@@
 
+TODO DELETE~\cite{ipv4sta}\endnote{Endnote}
+
 \section*{Acknowledgements}
-- Thank prof/TA
-TODO~\cite{ipv4sta}\endnote{Endnote}
+We would like to thank Louis DeKoven and Stefan Savage for their help and support throughout this project.
 

### 2017-06-10 docs/paper.tex
Methodology (draft)

--- 2017-06-06 docs/paper.tex
@@
 \documentclass[letterpaper,twocolumn,10pt]{article}
-\usepackage{usenix,epsfig,endnotes}
+\usepackage{url,epsfig}
 \begin{document}
@@
 \includegraphics[height=\baselineskip]{title}
-\\ \vspace{0.025 in} \large \normalfont
+\\ \vspace{0.65mm} \large \normalfont
 CSE 227: Computer Security - Spring 2017 \\ \textit{
@@
 \section{Methodology}
-TODO
-- Introduction to the methodology
-- Subsection: data collection
-- Subsection: data pre-processing
-- Subsection: clustering, confusables algorithm
-- Subsection: manual classification, guidelines used
+Our data collection involves two primary sources.
+The first one is a snapshot of the \texttt{.com} and \texttt{.net} domain zone, from now on referenced as \textit{.com snapshot}.
+This snapshot was provided by Verisign\footnote{\url{https://www.verisign.com/en_US/channel-resources/domain-registry-products/zone-file/index.xhtml}}, and it is dated on 2017/05/01.
+It contains, mostly, the name servers of all \texttt{.com} and \texttt{.net} domains.
+For the purposes of this project, only the \texttt{.com} domains were considered.
+
+The second data source is the \textit{Alexa Top 1 million sites ranking}\footnote{\url{https://www.alexa.com/topsites}}, from now on referenced as \textit{top domains snapshot}.
+It contains the most popular one million web sites, regardless whether they are \texttt{.com} domains or not.
+It was also retrieved on 2017/05/01.
+
+In an effort to help with the reproducibility and replicability of this project, the original data and processing code used in this project has been made available in a public repository\footnote{\url{https://github.com/jsidrach/idn-homograph-attack}}.
+
+\subsection{Data Preprocessing}
+We used the \textit{.com snapshot} to obtain all the international domains of the \texttt{.com} domain zone.
+All international domain names are represented using Punycode, so they start with the \texttt{xn--} prefix.
+Using this information we first filtered the \textit{.com snapshot} to match only the \texttt{.com} domains that start with \texttt{xn--}.
+Since the \textit{.com snapshot} contains name server records, a single domain may have more than one entry in the file.
+Only the domain name is relevant for this project, so the rest of the columns of the \textit{.com snapshot} were discarded.
+We sorted the domains in lexicographic order, removing duplicates in the process.
+
+We used the \textit{top domains snapshot} as a source for the canonical (non-international) domain name of a website, based on its ranking.
+As we were only interested in non-international domain names, so we discarded the ones that start with the preffix \texttt{xn--}.
+We also removed sub-domains, as we only had top level domain names in the \textit{.com snapshot}.
+
+\subsection{Clustering}
+The underlying assumptions behind the clustering process are that homograph attacks are more likely to target popular domains, and that the million domains from the \textit{top domains snapshot} contains most of the popular domains.
+To detect potential international domain name homograph attacks, we cluster the international domain names in the \textit{.com snapshot}.
+The representative of each cluster is a homograph domain name from the \textit{top domains snapshot}.
+Only clusters with more than one domain name are output.
+
+The detection of homograph domain names is done using an algorithm to check if two strings are confusable.
+This algorithm is described in the \textit{Unicode Technical Standard \#39}\footnote{\url{http://www.unicode.org/reports/tr39/#Confusable_Detection}}.
+The approach followed has some caveats, that could be addressed in future work.
+For instance, it does not detect a homograph of \texttt{www.google.com}, where the first ``.'' has been replaced by a similar looking unicode character.
+More sophisticated homographs can also be generated by using unicode characters similar to ``/''.
+It is also worth noting that only domain names from the \texttt{.com} zone were considered, but similar studies could be done to other top level domains following the same procedure.
+All things considered, we still think this approach is a valuable first step.
+
+Another type of clustering was also performed.
+We grouped the homograph domain names by its registrant organization, and ranked each organization by the number of homograph domain names to their name.
+This could shed light on which registrant organizations are allowing homograph domain names, or even on which indivuduals and companies are doing it the most.
+
+\subsection{Manual Classification}
+The last part of the data processing was the classification of the homograph domain names.
+This classification was done manually, to be able to differentiate between scam and unrelated websites.
+Some domains expired at the time of the classification, and were subsequently deleted from the output file.
+
+The two high level categories that were defined are \textit{Canonical} and \textit{Third Party}.
+The first one, \textit{Canonical}, is employed when the domain is registered by the same organization as its canonical homograph domain name.
+The second one, \textit{Third Party}, is used when the domain is registered by a different organization than its canonical homograph domain name.
+Additionally, a more detailed classification was made:
+\itemize{
+\setlength{\itemsep}{0pt}
+\setlength{\parskip}{0pt}
+\setlength{\parsep}{0pt}
+\item \textit{Canonical - Parking}: domain is registered but not accessible via HTTP.
+\item \textit{Canonical - Redirect}: domain redirects (HTTP Status Code 301/307/308) to its canonical homograph domain name.
+\item \textit{Third Party - Redirect to Canonical:} domain redirects (HTTP Status Code 301/307/308) to its canonical homograph domain name.
+\item \textit{Third Party - Unrelated}: domain resolves, but the contents of the website are totally unrelated to its canonical homograph domain name.
+\item \textit{Third Party - Parking}: domain is registered, but no accessible via HTTP, or when accessed, a default domain parking webpage is displayed.
+\item \textit{Third Party - Scam}: domain resolves, and the website displayed is a clear attempt (similar color, logos, etc.) to make users think they are visiting the canonical homograph domain name.
+}
 
@@
 TODO
-- Different results obtained
+- Comment different results obtained
+- Explain consequences of caveats (low number of matches)
+- Explain and reference tables
+- Some other interesting results (topic-related domain hoarding)
+
+\begin{table*}[]
+\centering
+\begin{tabular}{lrr}
+\hline
+Domains                                       & \#                         & \%                         \\ \hline
+\itshape\sffamily{Canonical domain names}     & \itshape\sffamily{458731}  & \itshape\sffamily{8.31\%}  \\
+\hspace{0.5cm} With IDN homographs            & 825                        & 6.04\%                     \\
+\hspace{0.5cm} Without IDN homograpphs        & 457906                     & 2.27\%                     \\
+\itshape\sffamily{International Domain Names} & \itshape\sffamily{1045400} & \itshape\sffamily{91.69\%} \\
+\hspace{0.5cm} With canonical homograph       & 1099                       & 3.68\%                     \\
+\hspace{0.5cm} Without canonical homograph    & 1044301                    & 2.74\%                     \\ \hline
+\end{tabular}
+\caption{Overview of the clustering results.}
+\label{clustering-results}
+\end{table*}
+
+\begin{table}[]
+\centering
+\begin{tabular}{lr}
+\hline
+Domain       & \# of IDN homographs \\ \hline
+google.com   & 24                   \\
+youtube.com  & 3                    \\
+facebook.com & 9                    \\
+baidu.com    & 3                    \\
+yahoo.com    & 4                    \\
+reddit.com   & 1                    \\
+qq.com       & 2                    \\
+taobao.com   & 1                    \\
+live.com     & 1                    \\
+vk.com       & 6                    \\ \hline
+\end{tabular}
+\caption{Top ten .com domains in the Alexa ranking with IDN homographs.}
+\label{top-com-alexa-with-idns}
+\end{table}
+
+\begin{table}[]
+\centering
+\begin{tabular}{lrr}
+\hline
+Status                               & \#                     & \%                         \\ \hline
+\itshape\sffamily{Canonical}         & \itshape\sffamily{88}  & \itshape\sffamily{8.31\%}  \\
+\hspace{0.5cm} Parking               & 64                     & 6.04\%                     \\
+\hspace{0.5cm} Redirect              & 24                     & 2.27\%                     \\
+\itshape\sffamily{Third Party}       & \itshape\sffamily{971} & \itshape\sffamily{91.69\%} \\
+\hspace{0.5cm} Redirect to Canonical & 39                     & 3.68\%                     \\
+\hspace{0.5cm} Unrelated             & 29                     & 2.74\%                     \\
+\hspace{0.5cm} Parking               & 872                    & 82.34\%                    \\
+\hspace{0.5cm} Scam                  & 31                     & 2.93\%                     \\ \hline
+\end{tabular}
+\caption{Breakdown of the manually classified homograph IDNs.}
+\label{manually-classified-idns}
+\end{table}
+
+TODO: mention:
+  Number of Third Party domains whose Registrant Organization and Email has than one homograph IDN registered: 437
+  Number of Registrant's Organization and Email that have more than one homograph IDN: 82
+
+\begin{table*}[]
+\centering
+\begin{tabular}{llr}
+\hline
+Registrant organization              & Registrant email           & \# of homograph IDNs \\ \hline
+Domains By Proxy, LLC                & --                         & 89                   \\
+Super Privacy Service c/o Dynadot    & privacy@dynadot.com        & 23                   \\
+Domain Registries Foundation         & --                         & 22                   \\
+Duong Thien                          & thiendv@outlook.com        & 18                   \\
+Syngenuity Limited                   & manager@syngenuity.com     & 12                   \\
+Helpnet: Brand Development \& Sales  & help@strongestbrands.com   & 12                   \\
+ONUNO L.L.C.                         & corucas@gmail.com          & 11                   \\
+Privacy Protection Service INC d/b/a & contact@privacyprotect.org & 10                   \\
+Hubertus Henz                        & hu\_h5@yahoo.de            & 9                    \\
+wuyu                                 & wy65535@126.com            & 7                    \\ \hline
+\end{tabular}
+\caption{Top ten registrants with the most homograph IDNs.}
+\label{top-registrants-homograph-idns}
+\end{table*}
 
@@
 - Possible future work
+- TLDs
+
+TODO DELETE~\cite{ipv4sta}
 
 \section*{Acknowledgements}
-- Thank prof/TA
-TODO~\cite{ipv4sta}\endnote{Endnote}
+We would like to thank Louis DeKoven and Stefan Savage for their help and support throughout this project.
 
@@
 
-\theendnotes
-
 \end{document}

### 2017-06-10 docs/paper.tex
intro and background

@@
 
+Domain names were originally designed to support only ASCII characters.
+The proposal of Internationalized Domain Name IDN) benefits non-English speaking people, however, it also presents the potential vulnerability.
+In this paper, we would analyze XXX top level .com domain
+by the means of clustering possible homograph domains and classify the owner of them.
+
 \section{Background}
@@
 - Browsers: display of IDNs, algorithms
+
+Domain name system contains the relationship between domain names with Internet Protocol(IP) address.
+It can can translate domain names to Internet Protocol(IP) address.
+At beginning, domain names support only ASCII characters.
+In 1996, Internationalized Domain Name (IDN) was proposed by Martin Drst for the purpose of letting non-English speaking people use Internet without additional restrictions.
+This extension involves representing Unicode characters in ASCII using Punycode, so that they could be then rendered back into their Unicode representation.
+Homograph letters (different letters whose representation is almost, if not, the same), however, present a potential vulnerability.
+For example, Cyrillic letter ’a’ can look identical to Latin letter ’a’ depending on the font.
+In other languages, like Chinese, there exists many homograph letters between traditional Chinese and simpli- fied Chinese.
+Malicious attackers can then register a domain where one of the letters is actually Cyrillic but whose representation matches a Latin one.
+Users could be linked to this newly registered malicious page, and they may not have any visual indication (at least without further interaction) that the page is not the one they think they are visiting.
+
+Currently, most popular website will show the hostname in Unicode depends on the language setting to defend IDN attack.
+For example, Chrome will display IDN in Unicode only if all characters of the domain names belong to only one language and this language has to be the user's preferred language.
 

### 2017-06-10 docs/paper.tex
Related work and reference update

@@
 \title{\Large
-\includegraphics[height=\baselineskip]{title}
+\includegraphics[height=\baselineskip]{title.png}
 \\ \vspace{0.65mm} \large \normalfont
@@
 The proposal of Internationalized Domain Name IDN) benefits non-English speaking people, however, it also presents the potential vulnerability.
-In this paper, we would analyze XXX top level .com domain
-by the means of clustering possible homograph domains and classify the owner of them.
+In this paper, we would analyze XXX top level .com domain by the means of clustering possible homograph domains and classify the owner of them.
 
@@
 For example, Cyrillic letter ’a’ can look identical to Latin letter ’a’ depending on the font.
-In other languages, like Chinese, there exists many homograph letters between traditional Chinese and simpli- fied Chinese.
+In other languages, like Chinese, there exists many homograph letters between traditional Chinese and simplified Chinese.
 Malicious attackers can then register a domain where one of the letters is actually Cyrillic but whose representation matches a Latin one.
@@
 - Brief analysis of previous papers on the same topic
+
+Many relevant studies have been conducted to show the vulnerability of IDN and provide possible solution to mitigate IDN homograph attack.
+In 2001, Evgeniy Gabrilovich and Alex Gontmakher has proved the feasibility of such attack based on the vulnerability of unicode in \textit{The Homograph Attack}~\cite{theHomoAttack}.
+In 2006, Vicktor Krammer proposed a defense mechanism based on address bar highlighting/indication technique and better UI of the browsers~\cite{phishdefenseKV}.
+His method of defense mainly target at regular users who do not neccessarily have relevant knowledge and through the better rendering of address along with explicit notification or alert on phishing url users would be aware of malicious website.
+Manurer and Höfer believed that safe guard based on browsers' blacklist is far from enough to protect users from sophisticated phishing attacks~\cite{proc-eds-2012}.
+They proposed an advanced method based on url components and spell checking functionality of search engine.
+In this method, an url would be divided into several components, namely, basename, subdomains, pathdomain, brandname.
+Each of this components will be sent to search engine as a term for spelling check and in the cases that spelling suggestion is returned the url will be counted as suspicious.
+The major browsers have their own IDN policies to defend against IDN homograph attack.
+Google Chrome, starting with Chrome 51, will display punycode if certain tests fail on the input url.
+These tests include but not limited to converting to unicode, less than one numbering systems involved, no invisible characters, etc.
+IE displays urls in IDN form if every component contains only characters from the languages configured in \textit{Internet Options}.
+Firefox uses a script mixing detection algorithm based on \textit{"Moderately Restrictive" profile of Unicode Technical Report 39} and displays unicode when url consists of any single script, any single script plus Latin, or it's in the whitelist of other combinations.
+Opera shows IDN only for whitelisted TLDs.
+Safari has a whitelist of scripts that do not contain confusable characters and only shows the IDN form for the whitelisted scripts.
 

### 2017-06-11 docs/paper.tex
Add more introduction

@@
 The proposal of Internationalized Domain Name IDN) benefits non-English speaking people, however, it also presents the potential vulnerability.
-In this paper, we would analyze XXX top level .com domain by the means of clustering possible homograph domains and classify the owner of them.
+
+In this paper, we would analyze XXX top level .com domain by means of clustering possible homograph domains and classifying the owner of them.
+In section 2, we talked about the background and history of Internationalied Domain Name (IDN) and the vulnerability behind it.
+In section 3, several relevant researches are briefly introduced, which provide a couple of possible solutions to address IDN homograph attack.
+We will also present the IDN policies of current major browsers in this section.
+Section 4 describes the methodology of data collection and analysis we adopt in this project.
+In the next section, we comment on different analysis results and explain the consequences of caveats.
+For the last section, we briefly explain the ethical considerations of the research.
 

### 2017-06-12 docs/paper.tex
Results draft

@@
 In this paper, we would analyze XXX top level .com domain by means of clustering possible homograph domains and classifying the owner of them.
-In section 2, we talked about the background and history of Internationalied Domain Name (IDN) and the vulnerability behind it.
+In section 2, we talked about the background and history of Internationalized Domain Name (IDN) and the vulnerability behind it.
 In section 3, several relevant researches are briefly introduced, which provide a couple of possible solutions to address IDN homograph attack.
@@
 Many relevant studies have been conducted to show the vulnerability of IDN and provide possible solution to mitigate IDN homograph attack.
-In 2001, Evgeniy Gabrilovich and Alex Gontmakher has proved the feasibility of such attack based on the vulnerability of unicode in \textit{The Homograph Attack}~\cite{theHomoAttack}.
+In 2001, Evgeniy Gabrilovich and Alex Gontmakher has proved the feasibility of such attack based on the vulnerability of Unicode in \textit{The Homograph Attack}~\cite{theHomoAttack}.
 In 2006, Vicktor Krammer proposed a defense mechanism based on address bar highlighting/indication technique and better UI of the browsers~\cite{phishdefenseKV}.
-His method of defense mainly target at regular users who do not neccessarily have relevant knowledge and through the better rendering of address along with explicit notification or alert on phishing url users would be aware of malicious website.
+His method of defense mainly target at regular users who do not necessarily have relevant knowledge and through the better rendering of address along with explicit notification or alert on phishing URL users would be aware of malicious website.
 Manurer and Höfer believed that safe guard based on browsers' blacklist is far from enough to protect users from sophisticated phishing attacks~\cite{proc-eds-2012}.
-They proposed an advanced method based on url components and spell checking functionality of search engine.
-In this method, an url would be divided into several components, namely, basename, subdomains, pathdomain, brandname.
-Each of this components will be sent to search engine as a term for spelling check and in the cases that spelling suggestion is returned the url will be counted as suspicious.
+They proposed an advanced method based on URL components and spell checking functionality of search engine.
+In this method, an URL would be divided into several components, namely, base name, sub-domains, path domain, brand name.
+Each of this components will be sent to search engine as a term for spelling check and in the cases that spelling suggestion is returned the URL will be counted as suspicious.
 The major browsers have their own IDN policies to defend against IDN homograph attack.
-Google Chrome, starting with Chrome 51, will display punycode if certain tests fail on the input url.
-These tests include but not limited to converting to unicode, less than one numbering systems involved, no invisible characters, etc.
-IE displays urls in IDN form if every component contains only characters from the languages configured in \textit{Internet Options}.
-Firefox uses a script mixing detection algorithm based on \textit{"Moderately Restrictive" profile of Unicode Technical Report 39} and displays unicode when url consists of any single script, any single script plus Latin, or it's in the whitelist of other combinations.
+Google Chrome, starting with Chrome 51, will display Punycode if certain tests fail on the input URL.
+These tests include but not limited to converting to Unicode, less than one numbering systems involved, no invisible characters, etc.
+IE displays URLs in IDN form if every component contains only characters from the languages configured in \textit{Internet Options}.
+Firefox uses a script mixing detection algorithm based on \textit{"Moderately Restrictive" profile of Unicode Technical Report 39} and displays Unicode when URL consists of any single script, any single script plus Latin, or it's in the white-list of other combinations.
 Opera shows IDN only for whitelisted TLDs.
@@
 
-\subsection{Data Preprocessing}
-We used the \textit{.com snapshot} to obtain all the international domains of the \texttt{.com} domain zone.
-All international domain names are represented using Punycode, so they start with the \texttt{xn--} prefix.
+\subsection{Data Processing}
+We used the \textit{.com snapshot} to obtain all the internationalized domains of the \texttt{.com} domain zone.
+All internationalized domain names are represented using Punycode, so they start with the \texttt{xn--} prefix.
 Using this information we first filtered the \textit{.com snapshot} to match only the \texttt{.com} domains that start with \texttt{xn--}.
@@
 We used the \textit{top domains snapshot} as a source for the canonical (non-international) domain name of a website, based on its ranking.
-As we were only interested in non-international domain names, so we discarded the ones that start with the preffix \texttt{xn--}.
+As we were only interested in non-internationalized domain names, so we discarded the ones that start with the prefix \texttt{xn--}.
 We also removed sub-domains, as we only had top level domain names in the \textit{.com snapshot}.
@@
 The underlying assumptions behind the clustering process are that homograph attacks are more likely to target popular domains, and that the million domains from the \textit{top domains snapshot} contains most of the popular domains.
-To detect potential international domain name homograph attacks, we cluster the international domain names in the \textit{.com snapshot}.
+To detect potential internationalized domain name homograph attacks, we cluster the internationalized domain names in the \textit{.com snapshot}.
 The representative of each cluster is a homograph domain name from the \textit{top domains snapshot}.
@@
 The approach followed has some caveats, that could be addressed in future work.
-For instance, it does not detect a homograph of \texttt{www.google.com}, where the first ``.'' has been replaced by a similar looking unicode character.
-More sophisticated homographs can also be generated by using unicode characters similar to ``/''.
+For instance, it does not detect a homograph of \texttt{www.google.com}, where the first ``.'' has been replaced by a similar looking Unicode character.
+More sophisticated homographs can also be generated by using Unicode characters similar to ``/''.
 It is also worth noting that only domain names from the \texttt{.com} zone were considered, but similar studies could be done to other top level domains following the same procedure.
@@
 We grouped the homograph domain names by its registrant organization, and ranked each organization by the number of homograph domain names to their name.
-This could shed light on which registrant organizations are allowing homograph domain names, or even on which indivuduals and companies are doing it the most.
+This could shed light on which registrant organizations are allowing homograph domain names, or even on which individuals and companies are doing it the most.
 
@@
 \item \textit{Third Party - Unrelated}: domain resolves, but the contents of the website are totally unrelated to its canonical homograph domain name.
-\item \textit{Third Party - Parking}: domain is registered, but no accessible via HTTP, or when accessed, a default domain parking webpage is displayed.
+\item \textit{Third Party - Parking}: domain is registered, but no accessible via HTTP, or when accessed, a default domain parking web page is displayed.
 \item \textit{Third Party - Scam}: domain resolves, and the website displayed is a clear attempt (similar color, logos, etc.) to make users think they are visiting the canonical homograph domain name.
@@
 \section{Results}
-TODO
-- Comment different results obtained
-- Explain consequences of caveats (low number of matches)
-- Explain and reference tables
-- Some other interesting results (topic-related domain hoarding)
 
-\begin{table*}[]
+\begin{table*}[ht!]
 \centering
@@
 \hspace{0.5cm} With IDN homographs                & 825                        & 6.04\%                     \\
-\hspace{0.5cm} Without IDN homograpphs        & 457906                     & 2.27\%                     \\
-\itshape\sffamily{International Domain Names} & \itshape\sffamily{1045400} & \itshape\sffamily{91.69\%} \\
+\hspace{0.5cm} Without IDN homographs             & 457906                     & 2.27\%                     \\
+\itshape\sffamily{Internationalized Domain Names} & \itshape\sffamily{1045400} & \itshape\sffamily{91.69\%} \\
 \hspace{0.5cm} With canonical homograph           & 1099                       & 3.68\%                     \\
@@
 
-\begin{table}[]
+We obtained 458731 domain names from the \textit{top domains snapshot} that belonged to the \texttt{.com} zone.
+From the \textit{.com snapshot}, we identified a total of 1044301 internationalized domains.
+However, only a low percentage of the internationalized domain names (3.68\%) had a homograph canonical domain name in the \textit{top domains snapshot}.
+Even if we take into account that our homograph detection algorithm is rather limited (as described before), these results still indicate that the majority of internationalized domain names are not being used in homograph attacks.
+An overview of these clustering results can be found in Table~\ref{clustering-results}.
+
+Table~\ref{top-com-alexa-with-idns} shows the number of internationalized domain name homographs for the top ten \texttt{.com} domains.
+It is worth noting that most of the homograph domains of \textit{google.com} are actually registered by Google, possibly as a defensive measure.
+Another surprising result of the homograph clustering is that 81.87\% of the groups have just one homograph internationalized domain name.
+This suggests that this kind of attack may not be targeted only to top websites, but rather to any domain where valuable information could be obtained from the users by a scam.
+
+\begin{table}[ht!]
 \centering
@@
 
-\begin{table}[]
+The manual classification sheds some light on how these homograph internationalized domain names are being used.
+For the most part (82.34\%), the domains are registered by a third party, and not being used actively (parking).
+One possible explanation for this is that the domain was bought in an attempt to be re-sold later at a higher price to the owner of the canonical homograph domain.
+A detailed breakdown of this classification can be found in Table~\ref{manually-classified-idns}.
+
+\begin{table}[ht!]
 \centering
@@
 
-TODO: mention:
-  Number of Third Party domains whose Registrant Organization and Email has than one homograph IDN registered: 437
-  Number of Registrant's Organization and Email that have more than one homograph IDN: 82
+Table~\ref{top-registrants-homograph-idns} contains the top ten registrants with the most homograph internationalized domain names.
+Most of these registrants are actually domain privacy companies, so it is impossible to know if the domains belong to the same person or not.
+There are also several individuals with a high number of homograph internationalized domain names.
+It is also worth mentioning that some of these individuals seem to be targeting specific industries.
+For instance, a single person has registered homographs of ``audi'', ``citroen'' and ``diesel''.
 
-\begin{table*}[]
+\begin{table*}[!ht]
 \centering
@@
 TODO
+- Publicly available information
+- Delay between whois to not saturate server, also only in small subset (about 1k domains)
 - Brief explanation why this research is ethical
@@
 
-\section*{Acknowledgements}
+\section*{Acknowledgments}
 We would like to thank Louis DeKoven and Stefan Savage for their help and support throughout this project.

### 2017-06-12 docs/paper.tex
Expanding related work and fix a few syntax

--- 2017-06-11 docs/paper.tex
@@
 
-Currently, most popular website will show the hostname in Unicode depends on the language setting to defend IDN attack.
-For example, Chrome will display IDN in Unicode only if all characters of the domain names belong to only one language and this language has to be the user's preferred language.
+Currently, most popular browsers will show the hostname in Unicode depends on the language setting to defend IDN attack.
+For example, Google Chrome\footnote{\url{https://www.google.com/chrome}} will display IDN in Unicode only if all characters of the domain names belong to only one language and this language has to be the user's preferred language.
 
@@
 His method of defense mainly target at regular users who do not neccessarily have relevant knowledge and through the better rendering of address along with explicit notification or alert on phishing url users would be aware of malicious website.
+This method check each character in an url seperately, highlighting digits or characters of various scripts in different background color so that users will be aware of the difference.
+It also suggest using larger font size in the address bar to help distinguish possible homograph characters from the Latin letter and alerting users when multiscript is detected by means of scripts block\footnote{\url{http://www.unicode.org/reports/tr24/}}.
+His proposal was innovative in his year but not entirely accurate because characters from the same script may be in different blocks while characters from different scripts sometimes lie in the same block.
 Manurer and Höfer believed that safe guard based on browsers' blacklist is far from enough to protect users from sophisticated phishing attacks~\cite{proc-eds-2012}.
@@
 Each of this components will be sent to search engine as a term for spelling check and in the cases that spelling suggestion is returned the url will be counted as suspicious.
+
 The major browsers have their own IDN policies to defend against IDN homograph attack.
@@
 These tests include but not limited to converting to unicode, less than one numbering systems involved, no invisible characters, etc.
-IE displays urls in IDN form if every component contains only characters from the languages configured in \textit{Internet Options}.
-Firefox uses a script mixing detection algorithm based on \textit{"Moderately Restrictive" profile of Unicode Technical Report 39} and displays unicode when url consists of any single script, any single script plus Latin, or it's in the whitelist of other combinations.
-Opera shows IDN only for whitelisted TLDs.
-Safari has a whitelist of scripts that do not contain confusable characters and only shows the IDN form for the whitelisted scripts.
+Internet Explorer\footnote{\url{https://support.microsoft.com/en-us/help/17621/internet-explorer-downloads}} displays urls in IDN form if every component contains only characters from the languages configured in \textit{Internet Options}.
+Firefox\footnote{\url{https://www.mozilla.org/en-US/firefox/new/}} uses a script mixing detection algorithm based on \textit{"Moderately Restrictive" profile of Unicode Technical Report 39} and displays unicode when url consists of any single script, any single script plus Latin, or it's in the whitelist of other combinations.
+Opera\footnote{\url{http://www.opera.com}} shows IDN only for whitelisted TLDs.
+Safari\footnote{\url{https://www.apple.com/safari}} has a whitelist of scripts that do not contain confusable characters and only shows the IDN form for the whitelisted scripts.
 

### 2017-06-12 docs/paper.tex
Introduction, ethics

--- 2017-06-12 docs/paper.tex
@@
 \section{Introduction}
-TODO
-- Introduction to the problem
-- Enumeration of sections this paper talks about
-
-Domain names were originally designed to support only ASCII characters.
-The proposal of Internationalized Domain Name IDN) benefits non-English speaking people, however, it also presents the potential vulnerability.
-
-In this paper, we would analyze XXX top level .com domain by means of clustering possible homograph domains and classifying the owner of them.
-In section 2, we talked about the background and history of Internationalized Domain Name (IDN) and the vulnerability behind it.
-In section 3, several relevant researches are briefly introduced, which provide a couple of possible solutions to address IDN homograph attack.
-We will also present the IDN policies of current major browsers in this section.
-Section 4 describes the methodology of data collection and analysis we adopt in this project.
-In the next section, we comment on different analysis results and explain the consequences of caveats.
-For the last section, we briefly explain the ethical considerations of the research.
-
-\section{Background}
-TODO
-- DNS: explanation
-- IDN: history, explanation
-- Browsers: display of IDNs, algorithms
-
-Domain name system contains the relationship between domain names with Internet Protocol(IP) address.
-It can can translate domain names to Internet Protocol(IP) address.
-At beginning, domain names support only ASCII characters.
-In 1996, Internationalized Domain Name (IDN) was proposed by Martin Drst for the purpose of letting non-English speaking people use Internet without additional restrictions.
+Domain names were originally designed to only support ASCII characters.
+Internationalized Domain Names (IDNs) were proposed back in December 1996 by Martin D\"{u}rst for the purpose of letting non-English speaking people use Internet without additional restrictions.
 This extension involves representing Unicode characters in ASCII using Punycode, so that they could be then rendered back into their Unicode representation.
 Homograph letters (different letters whose representation is almost, if not, the same), however, present a potential vulnerability.
-For example, Cyrillic letter ’a’ can look identical to Latin letter ’a’ depending on the font.
+For example, Cyrillic letter ``a'' can look identical to Latin letter ``a'' depending on the font.
 In other languages, like Chinese, there exists many homograph letters between traditional Chinese and simplified Chinese.
@@
 
-Currently, most popular website will show the hostname in Unicode depends on the language setting to defend IDN attack.
-For example, Chrome will display IDN in Unicode only if all characters of the domain names belong to only one language and this language has to be the user's preferred language.
+In this paper, we analyze the impact of this attack.
+Section 2 explains past and present policies of major browsers and top level domain registrants in an attempt to prevent the attack.
+Section 3 explores relevant work in the literature related to homograph attacks.
+Section 4 describes the methodology of data collection and analysis adopted in this project.
+Section 5 comments the different results obtained.
+Section 6 addresses the ethical concerns regarding the data collection.
+Section 7 presents the conclusions obtained from this project.
+
+\section{Background}
+TODO
+- Browsers policy
+- TLDs policy
 
@@
 This classification was done manually, to be able to differentiate between scam and unrelated websites.
+To help with the classification and speed up the process, we queried the \textit{WHOIS} records~\footnote{\url{https://whois.icann.org}} of every homograph domain name.
 Some domains expired at the time of the classification, and were subsequently deleted from the output file.
@@
 
-\begin{table*}[!ht]
+\begin{table*}[ht!]
 \centering
@@
 \section{Ethical Considerations}
-TODO
-- Publicly available information
-- Delay between whois to not saturate server, also only in small subset (about 1k domains)
-- Brief explanation why this research is ethical
+The domain information used in this project is publicly available and was voluntarily provided by the registrants of the domains.
+The full \texttt{.com} domain zone snapshot won't be publicly disclosed, as its access requires a paid subscription.
+The retrieval of the \textit{WHOIS} information was performed only for the homograph internationalized domain names, which were about one thousand.
+It was done with a significant delay between petitions (3 seconds) in order to avoid saturating the server.
 

### 2017-06-12 docs/paper.tex

--- 2017-06-12 docs/paper.tex
@@
 In 2006, Vicktor Krammer proposed a defense mechanism based on address bar highlighting/indication technique and better UI of the browsers~\cite{phishdefenseKV}.
-His method of defense mainly target at regular users who do not necessarily have relevant knowledge and through the better rendering of address along with explicit notification or alert on phishing URL users would be aware of malicious website.
+His method of defense mainly target at regular users who do not neccessarily have relevant knowledge and through the better rendering of address along with explicit notification or alert on phishing url users would be aware of malicious website.
+This method check each character in an url seperately, highlighting digits or characters of various scripts in different background color so that users will be aware of the difference.
+It also suggest using larger font size in the address bar to help distinguish possible homograph characters from the Latin letter and alerting users when multiscript is detected by means of scripts block\footnote{\url{http://www.unicode.org/reports/tr24/}}.
+His proposal was innovative in his year but not entirely accurate because characters from the same script may be in different blocks while characters from different scripts sometimes lie in the same block.
 Manurer and Höfer believed that safe guard based on browsers' blacklist is far from enough to protect users from sophisticated phishing attacks~\cite{proc-eds-2012}.
-They proposed an advanced method based on URL components and spell checking functionality of search engine.
-In this method, an URL would be divided into several components, namely, base name, sub-domains, path domain, brand name.
-Each of this components will be sent to search engine as a term for spelling check and in the cases that spelling suggestion is returned the URL will be counted as suspicious.
+They proposed an advanced method based on url components and spell checking functionality of search engine.
+In this method, an url would be divided into several subterms, namely, base name\footnote{The primary domain name as registered at the registrar}, subdomain\footnote{A part of the primary domain}, path domain\footnote{A subfolder of the url}, brand name\footnote{A brand name that occurs in a url}.
+Their algorithm is based on the following characteristics on different subterms of url:
+\begin{itemize}
+  \item Base name: Phisher cannot register the original domain but can only register mispelling or homograph domain name because the original one is often registered ahead by the company.
+  \item Subdomain: Phisher can prepend subdomain to the primary domain being attacked to fool users into thinking that they are on the real domain.
+One example would be \url{http://us.battle.net.loginaccoutbattle.net/login/en/login.html}.
+  \item Path domain: Phisher sometimes place a second domain as a subfolder of the url path, usually right after the primary domain name, for instance, \url{http://piasel.altervista.org/www.paypal.com/new/paypal/intl/update}.
+  \item Brand name: There are cases that only the brand name is inserted somewhere in the URL to fool users.
+\end{itemize}
+Each of this components will be sent to search engine as a term for spelling check and in the cases that spelling suggestion is returned the url will be counted as suspicious.
+By splitting a url into these subterms, this method cover almost all possible cases of fake url or domain name.
+However, this mechanism is based on the search engine for return spelling suggestion and as a result, it does not play well when it is used as sole detection.
 The major browsers have their own IDN policies to defend against IDN homograph attack.
-Google Chrome, starting with Chrome 51, will display Punycode if certain tests fail on the input URL.
-These tests include but not limited to converting to Unicode, less than one numbering systems involved, no invisible characters, etc.
-IE displays URLs in IDN form if every component contains only characters from the languages configured in \textit{Internet Options}.
-Firefox uses a script mixing detection algorithm based on \textit{"Moderately Restrictive" profile of Unicode Technical Report 39} and displays Unicode when URL consists of any single script, any single script plus Latin, or it's in the white-list of other combinations.
-Opera shows IDN only for whitelisted TLDs.
-Safari has a whitelist of scripts that do not contain confusable characters and only shows the IDN form for the whitelisted scripts.
+Google Chrome, starting with Chrome 51, will display punycode if certain tests fail on the input url.
+These tests include but not limited to converting to unicode, less than one numbering systems involved, no invisible characters, etc.
+Internet Explorer\footnote{\url{https://support.microsoft.com/en-us/help/17621/internet-explorer-downloads}} displays urls in IDN form if every component contains only characters from the languages configured in \textit{Internet Options}.
+Firefox\footnote{\url{https://www.mozilla.org/en-US/firefox/new/}} uses a script mixing detection algorithm based on \textit{"Moderately Restrictive" profile of Unicode Technical Report 39} and displays unicode when url consists of any single script, any single script plus Latin, or it's in the whitelist of other combinations.
+Opera\footnote{\url{http://www.opera.com}} shows IDN only for whitelisted TLDs.
+Safari\footnote{\url{https://www.apple.com/safari}} has a whitelist of scripts that do not contain confusable characters and only shows the IDN form for the whitelisted scripts.
 

### 2017-06-12 docs/paper.tex

@@
 
+In this paper, we analyze the impact of this attack.
+Section 2 explains past and present policies of major browsers and top level domain(TLD) registrants in an attempt to prevent the attack.
+Section 3 explores relevant work in the literature related to homograph attacks.
+Section 4 describes the methodology of data collection and analysis adopted in this project.
+Section 5 comments the different results obtained.
+Section 6 addresses the ethical concerns regarding the data collection.
+Section 7 presents the conclusions obtained from this project.
+
+\section{Background}
+TODO
+- Browsers policy
+- TLDs policy
+
+\subsection{Browsers Policy}
+The major browsers have their own IDN policies to defend against IDN homograph attack.
+Google Chrome, starting with Chrome 51, will display punycode if certain tests fail on the input url.
+These tests include but not limited to converting to unicode, less than one numbering systems involved, no invisible characters, etc.
+Internet Explorer\footnote{\url{https://support.microsoft.com/en-us/help/17621/internet-explorer-downloads}} displays urls in IDN form if every component contains only characters from the languages configured in \textit{Internet Options}.
+Firefox\footnote{\url{https://www.mozilla.org/en-US/firefox/new/}} uses a script mixing detection algorithm based on \textit{"Moderately Restrictive" profile of Unicode Technical Report 39} and displays unicode when url consists of any single script, any single script plus Latin, or it's in the whitelist of other combinations.
+Opera\footnote{\url{http://www.opera.com}} shows IDN only for whitelisted TLDs.
+Safari\footnote{\url{https://www.apple.com/safari}} has a whitelist of scripts that do not contain confusable characters and only shows the IDN form for the whitelisted scripts.
+
+\subsection{TLDs Policy}
+
 \section{Related Work}
@@
 Many relevant studies have been conducted to show the vulnerability of IDN and provide possible solution to mitigate IDN homograph attack.
+
 In 2001, Evgeniy Gabrilovich and Alex Gontmakher has proved the feasibility of such attack based on the vulnerability of Unicode in \textit{The Homograph Attack}~\cite{theHomoAttack}.
+
 In 2006, Vicktor Krammer proposed a defense mechanism based on address bar highlighting/indication technique and better UI of the browsers~\cite{phishdefenseKV}.
@@
 His proposal was innovative in his year but not entirely accurate because characters from the same script may be in different blocks while characters from different scripts sometimes lie in the same block.
+
 Manurer and Höfer believed that safe guard based on browsers' blacklist is far from enough to protect users from sophisticated phishing attacks~\cite{proc-eds-2012}.
@@
 By splitting a url into these subterms, this method cover almost all possible cases of fake url or domain name.
-However, this mechanism is based on the search engine for return spelling suggestion and as a result, it does not play well when it is used as sole detection.
-The major browsers have their own IDN policies to defend against IDN homograph attack.
-Google Chrome, starting with Chrome 51, will display punycode if certain tests fail on the input url.
-These tests include but not limited to converting to unicode, less than one numbering systems involved, no invisible characters, etc.
-Internet Explorer\footnote{\url{https://support.microsoft.com/en-us/help/17621/internet-explorer-downloads}} displays urls in IDN form if every component contains only characters from the languages configured in \textit{Internet Options}.
-Firefox\footnote{\url{https://www.mozilla.org/en-US/firefox/new/}} uses a script mixing detection algorithm based on \textit{"Moderately Restrictive" profile of Unicode Technical Report 39} and displays unicode when url consists of any single script, any single script plus Latin, or it's in the whitelist of other combinations.
-Opera\footnote{\url{http://www.opera.com}} shows IDN only for whitelisted TLDs.
-Safari\footnote{\url{https://www.apple.com/safari}} has a whitelist of scripts that do not contain confusable characters and only shows the IDN form for the whitelisted scripts.
+However, this mechanism is based on the search engine for return spelling suggestion and as a result, it does not perform well when it is used as sole detection.
 

### 2017-06-12 docs/paper.tex
Insert screenshot into introduction
Abstract + keyword

@@
 \usepackage{url,epsfig}
+\providecommand{\keywords}[1]{\textbf{\textit{Keywords:}} #1}
+
 \begin{document}
@@
 
-\abstract{TODO}
+\abstract{
+The invention of unicode made it possible for non-English speaking people to enter the world of Internet.
+However, it also open up the possibilities of malicious use of url.
+Sometimes different letters from different languages can look almost the same depending on the font.
+This paper mainly summarize the previous relevant work and analyze the current circumstance of Internationalized Domain Name Homograph Attack on the Internet via statistical approach on the websites from Alexa top 1 million rankings.
+Through the analysis results we will be able to provide some insight on this subject.
+}
+
+\keywords{IDN, homograph, Alexa, statistics analysis} %Maybe more? or reduncdant?
 
@@
 For example, Google Chrome\footnote{\url{https://www.google.com/chrome}} will display IDN in Unicode only if all characters of the domain names belong to only one language and this language has to be the user's preferred language.
+\ref{screenshot} show the screenshots of the original url of \url{www.google.com} and its homograph.
+
+\begin{figure}[t]
+  \includegraphics[width=\linewidth]{google.png}
+  \includegraphics[width=\linewidth]{fakegoogle.png}
+  \centering
+  \caption{Google(top) and its homograph(bottom) on Chrome}
+  \label{screenshot}
+\end{figure}
 

### 2017-06-12 docs/paper.tex
Review sections 1, 3, 4, 5, 6. Left: abstract, background, related work, conclusions

--- 2017-06-12 docs/paper.tex
@@
 \author{
-{\rm Chen Lai}\\
+{\rm Chen Lai\footnote{Author names are ordered lexicographically, by last name.}}\\
 \normalfont{\texttt{chl588@ucsd.edu}}
 \and
-{\rm Zhongrong Jian}\\
+{\rm Zhongrong Jian\footnotemark[\value{footnote}]}\\
 \normalfont{\texttt{zhjian@ucsd.edu}}
 \and
-{\rm J. Sidrach}\\
+{\rm J. Sidrach\footnotemark[\value{footnote}]}\\
 \normalfont{\texttt{jsidrach@ucsd.edu}}
@@
 Domain names were originally designed to only support ASCII characters.
-Internationalized Domain Names (IDNs) were proposed back in December 1996 by Martin D\"{u}rst for the purpose of letting non-English speaking people use Internet without additional restrictions.
+Internationalized Domain Names (IDNs) were proposed back in December 1996 by Martin D\"{u}rst\footnote{\url{https://tools.ietf.org/html/draft-duerst-dns-i18n-00}} for the purpose of letting non-English speaking people use Internet without additional restrictions.
 This extension involves representing Unicode characters in ASCII using Punycode, so that they could be then rendered back into their Unicode representation.
-Homograph letters (different letters whose representation is almost, if not, the same), however, present a potential vulnerability.
+Homograph letters (different letters whose representation is almost, if not, the same), however, present a potential security vulnerability.
 For example, Cyrillic letter ``a'' can look identical to Latin letter ``a'' depending on the font.
 In other languages, like Chinese, there exists many homograph letters between traditional Chinese and simplified Chinese.
-Malicious attackers can then register a domain where one of the letters is actually Cyrillic but whose representation matches a Latin one.
+Malicious attackers could then register a domain where one of the letters is actually Cyrillic but whose representation matched a Latin one.
 Users could be linked to this newly registered malicious page, and they may not have any visual indication (at least without further interaction) that the page is not the one they think they are visiting.
 
-Currently, most popular browsers will show the hostname in Unicode depends on the language setting to defend IDN attack.
-For example, Google Chrome\footnote{\url{https://www.google.com/chrome}} will display IDN in Unicode only if all characters of the domain names belong to only one language and this language has to be the user's preferred language.
-
-In this paper, we analyze the impact of this attack.
-Section 2 explains past and present policies of major browsers and top level domain(TLD) registrants in an attempt to prevent the attack.
+In this paper, we analyze the potential impact of this type of attack, commonly refered to as IDN Homograph Attack.
+Section 2 explains past and present policies of major browsers and top-level domain (TLD) registrants in an attempt to prevent the attack.
 Section 3 explores relevant work in the literature related to homograph attacks.
@@
 - TLDs policy
+
+Currently, most popular browsers will show the hostname in Unicode depends on the language setting to defend IDN attack.
+For example, Google Chrome\footnote{\url{https://www.google.com/chrome}} will display IDN in Unicode only if all characters of the domain names belong to only one language and this language has to be the user's preferred language.
+\ref{screenshot} show the screenshots of the original url of \url{www.google.com} and its homograph.
+
+\begin{figure}[t]
+  \includegraphics[width=\linewidth]{google.png}
+  \includegraphics[width=\linewidth]{fakegoogle.png}
+  \centering
+  \caption{Google(top) and its homograph(bottom) on Chrome}
+  \label{screenshot}
+\end{figure}
 
@@
 \section{Methodology}
-Our data collection involves two primary sources.
-The first one is a snapshot of the \texttt{.com} and \texttt{.net} domain zone, from now on referenced as \textit{.com snapshot}.
+Our data collection involved two primary sources.
+The first one was a snapshot of the \texttt{.com} and \texttt{.net} domain zone, from now on referenced as \textit{.com snapshot}.
 This snapshot was provided by Verisign\footnote{\url{https://www.verisign.com/en_US/channel-resources/domain-registry-products/zone-file/index.xhtml}}, and it is dated on 2017/05/01.
-It contains, mostly, the name servers of all \texttt{.com} and \texttt{.net} domains.
+It contains, for the most part, the name servers of all \texttt{.com} and \texttt{.net} domains.
 For the purposes of this project, only the \texttt{.com} domains were considered.
 
-The second data source is the \textit{Alexa Top 1 million sites ranking}\footnote{\url{https://www.alexa.com/topsites}}, from now on referenced as \textit{top domains snapshot}.
-It contains the most popular one million web sites, regardless whether they are \texttt{.com} domains or not.
+The second data source was the \textit{Alexa Top 1 million sites ranking}\footnote{\url{https://www.alexa.com/topsites}}, from now on referenced as \textit{top domains snapshot}.
+It contains the most popular one million web sites (as ranked by Alexa), regardless whether they are \texttt{.com} domains or not.
 It was also retrieved on 2017/05/01.
@@
 Only the domain name is relevant for this project, so the rest of the columns of the \textit{.com snapshot} were discarded.
-We sorted the domains in lexicographic order, removing duplicates in the process.
+We sorted the domains in lexicographical order, removing duplicates in the process.
 
 We used the \textit{top domains snapshot} as a source for the canonical (non-international) domain name of a website, based on its ranking.
-As we were only interested in non-internationalized domain names, so we discarded the ones that start with the prefix \texttt{xn--}.
-We also removed sub-domains, as we only had top level domain names in the \textit{.com snapshot}.
+As we were only interested in non-internationalized domain names, we discarded the ones that start with the prefix \texttt{xn--}.
+We also removed sub-domains, since we only had top-level domain names in the \textit{.com snapshot}.
 
@@
 The underlying assumptions behind the clustering process are that homograph attacks are more likely to target popular domains, and that the million domains from the \textit{top domains snapshot} contains most of the popular domains.
-To detect potential internationalized domain name homograph attacks, we cluster the internationalized domain names in the \textit{.com snapshot}.
-The representative of each cluster is a homograph domain name from the \textit{top domains snapshot}.
-Only clusters with more than one domain name are output.
+To detect potential internationalized domain name homograph attacks, we clustered the internationalized domain names in the \textit{.com snapshot}.
+The representative of each cluster is a homograph domain name from the \textit{top domains snapshot}, which we called canonical domain name.
+Only clusters with at least one internationalized homograph domain name were output.
 
-The detection of homograph domain names is done using an algorithm to check if two strings are confusable.
+The detection of homograph domain names was done using an algorithm to check if two strings are confusable.
 This algorithm is described in the \textit{Unicode Technical Standard \#39}\footnote{\url{http://www.unicode.org/reports/tr39/#Confusable_Detection}}.
@@
 More sophisticated homographs can also be generated by using Unicode characters similar to ``/''.
-It is also worth noting that only domain names from the \texttt{.com} zone were considered, but similar studies could be done to other top level domains following the same procedure.
+It is also worth noting that only domain names from the \texttt{.com} zone were considered, but similar studies could be done to other top-level domains following the same procedure.
 All things considered, we still think this approach is a valuable first step.
@@
 This classification was done manually, to be able to differentiate between scam and unrelated websites.
-To help with the classification and speed up the process, we queried the \textit{WHOIS} records~\footnote{\url{https://whois.icann.org}} of every homograph domain name.
-Some domains expired at the time of the classification, and were subsequently deleted from the output file.
+To help with the classification and speed up the process, we queried the \textit{WHOIS} records\footnote{\url{https://whois.icann.org}} of every homograph domain name.
+Some domains had expired at the time of the classification, and were subsequently deleted from the output file.
 
 The two high level categories that were defined are \textit{Canonical} and \textit{Third Party}.
-The first one, \textit{Canonical}, is employed when the domain is registered by the same organization as its canonical homograph domain name.
-The second one, \textit{Third Party}, is used when the domain is registered by a different organization than its canonical homograph domain name.
+The first one, \textit{Canonical}, was employed when the domain is registered by the same organization as its canonical homograph domain name.
+The second one, \textit{Third Party}, was used when the domain is registered by a different organization than its canonical homograph domain name.
 Additionally, a more detailed classification was made:
@@
 \setlength{\parsep}{0pt}
-\item \textit{Canonical - Parking}: domain is registered but not accessible via HTTP.
-\item \textit{Canonical - Redirect}: domain redirects (HTTP Status Code 301/307/308) to its canonical homograph domain name.
-\item \textit{Third Party - Redirect to Canonical:} domain redirects (HTTP Status Code 301/307/308) to its canonical homograph domain name.
-\item \textit{Third Party - Unrelated}: domain resolves, but the contents of the website are totally unrelated to its canonical homograph domain name.
-\item \textit{Third Party - Parking}: domain is registered, but no accessible via HTTP, or when accessed, a default domain parking web page is displayed.
-\item \textit{Third Party - Scam}: domain resolves, and the website displayed is a clear attempt (similar color, logos, etc.) to make users think they are visiting the canonical homograph domain name.
+\item \textit{Canonical - Parking}: domain was registered but it was not accessible via HTTP.
+\item \textit{Canonical - Redirect}: domain redirected (HTTP Status Code 301/307/308) to its canonical homograph domain name.
+\item \textit{Third Party - Redirect to Canonical:} domain redirected (HTTP Status Code 301/307/308) to its canonical homograph domain name.
+\item \textit{Third Party - Unrelated}: domain resolved, but the contents of the website were totally unrelated to its canonical homograph domain name.
+\item \textit{Third Party - Parking}: domain was registered, but it was not accessible via HTTP, or when accessed, a default domain parking web page was displayed.
+\item \textit{Third Party - Scam}: domain resolved, and the website displayed was a clear attempt (similar color, logos, etc.) to make users think they were visiting the canonical homograph domain name.
 }
@@
 From the \textit{.com snapshot}, we identified a total of 1044301 internationalized domains.
-However, only a low percentage of the internationalized domain names (3.68\%) had a homograph canonical domain name in the \textit{top domains snapshot}.
+However, only a low percentage of the internationalized domain names (3.68\%) had a matching homograph canonical domain name in the \textit{top domains snapshot}.
 Even if we take into account that our homograph detection algorithm is rather limited (as described before), these results still indicate that the majority of internationalized domain names are not being used in homograph attacks.
@@
 
-The manual classification sheds some light on how these homograph internationalized domain names are being used.
+The manual classification sheds some light on how these homograph internationalized domain names are currently being used.
 For the most part (82.34\%), the domains are registered by a third party, and not being used actively (parking).
-One possible explanation for this is that the domain was bought in an attempt to be re-sold later at a higher price to the owner of the canonical homograph domain.
+One possible explanation for this is that the domain was bought in an attempt to be re-sold later at a higher price to the owner of the matching canonical homograph domain.
 A detailed breakdown of this classification can be found in Table~\ref{manually-classified-idns}.
@@
 \section{Ethical Considerations}
-The domain information used in this project is publicly available and was voluntarily provided by the registrants of the domains.
-The full \texttt{.com} domain zone snapshot won't be publicly disclosed, as its access requires a paid subscription.
+The domain information used in this project is publicly available, and was voluntarily provided by the registrants of the domains when they registered them.
+The full \texttt{.com} domain zone snapshot will not be publicly disclosed, as its access requires a paid subscription.
 The retrieval of the \textit{WHOIS} information was performed only for the homograph internationalized domain names, which were about one thousand.
-It was done with a significant delay between petitions (3 seconds) in order to avoid saturating the server.
+It was performed with a significant delay between petitions (3 seconds) in order to avoid saturating the servers.
 
@@
 - TLDs
-
-TODO DELETE~\cite{ipv4sta}
 

### 2017-06-12 src/whois_homographs.sh

@@ -18,5 +18,5 @@ while IFS="," read rank domain unicode punycode; do
     cdate="$(echo "$info" | grep -e "^Creation Date: " | cut -d " " -f 3-)"
     udate="$(echo "$info" | grep -e "^Updated Date: " | cut -d " " -f 3-)"
     printf "%s\t%s\t%s\t%s\t%s\t%s\t%s\t%s\n" "$rank" "$domain" "$unicode" "$punycode" "$org" "$email" "$cdate" "$udate"
-    sleep 1s
+    sleep 3s
 done < "../data/clustered-idns-20170501.csv"

### 2017-06-12 docs/paper.tex

@@
 
-\abstract{TODO}
+\abstract{
+The invention of Unicode made it possible for non-English speaking people to enter the world of Internet.
+However, it also open up the possibilities of malicious use of URL.
+Sometimes different letters from different languages can look almost the same depending on the font.
+This paper mainly summarize the previous relevant work and analyze the current circumstance of Internationalized Domain Name Homograph Attack on the Internet via statistical approach on the websites from Alexa top 1 million rankings.
+Through the analysis results we will be able to provide some insight on this subject.
+}
+
+\keywords{Internationalized Domain Names, Homograph Attack, Phishing, Unicode, Punycode, Browser, Computer Security.}
 
@@
 
-In this paper, we analyze the potential impact of this type of attack, commonly refered to as IDN Homograph Attack.
+In this paper, we analyze the potential impact of this type of attack, commonly referred to as IDN Homograph Attack.
 Section 2 explains past and present policies of major browsers and top-level domain (TLD) registrants in an attempt to prevent the attack.
@@
 
-Currently, most popular browsers will show the hostname in Unicode depends on the language setting to defend IDN attack.
+Currently, most popular browsers will show the host name in Unicode depends on the language setting to defend IDN attack.
 For example, Google Chrome\footnote{\url{https://www.google.com/chrome}} will display IDN in Unicode only if all characters of the domain names belong to only one language and this language has to be the user's preferred language.
-\ref{screenshot} show the screenshots of the original url of \url{www.google.com} and its homograph.
+\ref{screenshot} show the screenshots of the original URL of \url{www.google.com} and its homograph.
 
@@
 The major browsers have their own IDN policies to defend against IDN homograph attack.
-Google Chrome, starting with Chrome 51, will display punycode if certain tests fail on the input url.
-These tests include but not limited to converting to unicode, less than one numbering systems involved, no invisible characters, etc.
-Internet Explorer\footnote{\url{https://support.microsoft.com/en-us/help/17621/internet-explorer-downloads}} displays urls in IDN form if every component contains only characters from the languages configured in \textit{Internet Options}.
-Firefox\footnote{\url{https://www.mozilla.org/en-US/firefox/new/}} uses a script mixing detection algorithm based on \textit{"Moderately Restrictive" profile of Unicode Technical Report 39} and displays unicode when url consists of any single script, any single script plus Latin, or it's in the whitelist of other combinations.
+Google Chrome, starting with Chrome 51, will display Punycode if certain tests fail on the input URL.
+These tests include but not limited to converting to Unicode, less than one numbering systems involved, no invisible characters, etc.
+Internet Explorer\footnote{\url{https://support.microsoft.com/en-us/help/17621/internet-explorer-downloads}} displays URLs in IDN form if every component contains only characters from the languages configured in \textit{Internet Options}.
+Firefox\footnote{\url{https://www.mozilla.org/en-US/firefox/new/}} uses a script mixing detection algorithm based on \textit{"Moderately Restrictive" profile of Unicode Technical Report 39} and displays Unicode when URL consists of any single script, any single script plus Latin, or it's in the white-list of other combinations.
 Opera\footnote{\url{http://www.opera.com}} shows IDN only for whitelisted TLDs.
@@
 His method of defense mainly target at regular users who do not neccessarily have relevant knowledge and through the better rendering of address along with explicit notification or alert on phishing url users would be aware of malicious website.
-This method check each character in an url seperately, highlighting digits or characters of various scripts in different background color so that users will be aware of the difference.
-It also suggest using larger font size in the address bar to help distinguish possible homograph characters from the Latin letter and alerting users when multiscript is detected by means of scripts block\footnote{\url{http://www.unicode.org/reports/tr24/}}.
+This method check each character in an URL separately, highlighting digits or characters of various scripts in different background color so that users will be aware of the difference.
+It also suggest using larger font size in the address bar to help distinguish possible homograph characters from the Latin letter and alerting users when multi-script is detected by means of scripts block\footnote{\url{http://www.unicode.org/reports/tr24/}}.
 His proposal was innovative in his year but not entirely accurate because characters from the same script may be in different blocks while characters from different scripts sometimes lie in the same block.

### 2017-06-12 docs/paper.tex
Move notes to the end!

@@
 \documentclass[letterpaper,twocolumn,10pt]{article}
-\usepackage{url,epsfig}
+\usepackage{url,epsfig,endnotes}
 \providecommand{\keywords}[1]{\textbf{\textit{Keywords:}} #1}
@@
 \and
-{\rm J. Sidrach\footnotemark[\value{footnote}]}\\
+{\rm J. Sidrach\endnotemark[\value{endnote}]}\\
 \normalfont{\texttt{jsidrach@ucsd.edu}}
@@
 Domain names were originally designed to only support ASCII characters.
-Internationalized Domain Names (IDNs) were proposed back in December 1996 by Martin D\"{u}rst\footnote{\url{https://tools.ietf.org/html/draft-duerst-dns-i18n-00}} for the purpose of letting non-English speaking people use Internet without additional restrictions.
+Internationalized Domain Names (IDNs) were proposed back in December 1996 by Martin D\"{u}rst\endnote{\url{https://tools.ietf.org/html/draft-duerst-dns-i18n-00}} for the purpose of letting non-English speaking people use Internet without additional restrictions.
 This extension involves representing Unicode characters in ASCII using Punycode, so that they could be then rendered back into their Unicode representation.
@@
 Currently, most popular browsers will show the host name in Unicode depends on the language setting to defend IDN attack.
-For example, Google Chrome\footnote{\url{https://www.google.com/chrome}} will display IDN in Unicode only if all characters of the domain names belong to only one language and this language has to be the user's preferred language.
+For example, Google Chrome\endnote{\url{https://www.google.com/chrome}} will display IDN in Unicode only if all characters of the domain names belong to only one language and this language has to be the user's preferred language.
 \ref{screenshot} show the screenshots of the original URL of \url{www.google.com} and its homograph.
@@
 These tests include but not limited to converting to Unicode, less than one numbering systems involved, no invisible characters, etc.
-Internet Explorer\footnote{\url{https://support.microsoft.com/en-us/help/17621/internet-explorer-downloads}} displays URLs in IDN form if every component contains only characters from the languages configured in \textit{Internet Options}.
-Firefox\footnote{\url{https://www.mozilla.org/en-US/firefox/new/}} uses a script mixing detection algorithm based on \textit{"Moderately Restrictive" profile of Unicode Technical Report 39} and displays Unicode when URL consists of any single script, any single script plus Latin, or it's in the white-list of other combinations.
-Opera\footnote{\url{http://www.opera.com}} shows IDN only for whitelisted TLDs.
-Safari\footnote{\url{https://www.apple.com/safari}} has a whitelist of scripts that do not contain confusable characters and only shows the IDN form for the whitelisted scripts.
+Internet Explorer\endnote{\url{https://support.microsoft.com/en-us/help/17621/internet-explorer-downloads}} displays URLs in IDN form if every component contains only characters from the languages configured in \textit{Internet Options}.
+Firefox\endnote{\url{https://www.mozilla.org/en-US/firefox/new/}} uses a script mixing detection algorithm based on \textit{"Moderately Restrictive" profile of Unicode Technical Report 39} and displays Unicode when URL consists of any single script, any single script plus Latin, or it's in the white-list of other combinations.
+Opera\endnote{\url{http://www.opera.com}} shows IDN only for whitelisted TLDs.
+Safari\endnote{\url{https://www.apple.com/safari}} has a whitelist of scripts that do not contain confusable characters and only shows the IDN form for the whitelisted scripts.
 
@@
 This method check each character in an URL separately, highlighting digits or characters of various scripts in different background color so that users will be aware of the difference.
-It also suggest using larger font size in the address bar to help distinguish possible homograph characters from the Latin letter and alerting users when multi-script is detected by means of scripts block\footnote{\url{http://www.unicode.org/reports/tr24/}}.
+It also suggest using larger font size in the address bar to help distinguish possible homograph characters from the Latin letter and alerting users when multi-script is detected by means of scripts block\endnote{\url{http://www.unicode.org/reports/tr24/}}.
 His proposal was innovative in his year but not entirely accurate because characters from the same script may be in different blocks while characters from different scripts sometimes lie in the same block.
@@
 They proposed an advanced method based on url components and spell checking functionality of search engine.
-In this method, an url would be divided into several subterms, namely, base name\footnote{The primary domain name as registered at the registrar}, subdomain\footnote{A part of the primary domain}, path domain\footnote{A subfolder of the url}, brand name\footnote{A brand name that occurs in a url}.
+In this method, an url would be divided into several subterms, namely, base name\endnote{The primary domain name as registered at the registrar}, subdomain\endnote{A part of the primary domain}, path domain\endnote{A subfolder of the url}, brand name\endnote{A brand name that occurs in a url}.
 Their algorithm is based on the following characteristics on different subterms of url:
@@
 The first one was a snapshot of the \texttt{.com} and \texttt{.net} domain zone, from now on referenced as \textit{.com snapshot}.
-This snapshot was provided by Verisign\footnote{\url{https://www.verisign.com/en_US/channel-resources/domain-registry-products/zone-file/index.xhtml}}, and it is dated on 2017/05/01.
+This snapshot was provided by Verisign\endnote{\url{https://www.verisign.com/en_US/channel-resources/domain-registry-products/zone-file/index.xhtml}}, and it is dated on 2017/05/01.
 It contains, for the most part, the name servers of all \texttt{.com} and \texttt{.net} domains.
@@
 
-The second data source was the \textit{Alexa Top 1 million sites ranking}\footnote{\url{https://www.alexa.com/topsites}}, from now on referenced as \textit{top domains snapshot}.
+The second data source was the \textit{Alexa Top 1 million sites ranking}\endnote{\url{https://www.alexa.com/topsites}}, from now on referenced as \textit{top domains snapshot}.
 It contains the most popular one million web sites (as ranked by Alexa), regardless whether they are \texttt{.com} domains or not.
@@
 
-In an effort to help with the reproducibility and replicability of this project, the original data and processing code used in this project has been made available in a public repository\footnote{\url{https://github.com/jsidrach/idn-homograph-attack}}.
+In an effort to help with the reproducibility and replicability of this project, the original data and processing code used in this project has been made available in a public repository\endnote{\url{https://github.com/jsidrach/idn-homograph-attack}}.
 
@@
 The detection of homograph domain names was done using an algorithm to check if two strings are confusable.
-This algorithm is described in the \textit{Unicode Technical Standard \#39}\footnote{\url{http://www.unicode.org/reports/tr39/#Confusable_Detection}}.
+This algorithm is described in the \textit{Unicode Technical Standard \#39}\endnote{\url{http://www.unicode.org/reports/tr39}}.
 The approach followed has some caveats, that could be addressed in future work.
@@
 This classification was done manually, to be able to differentiate between scam and unrelated websites.
-To help with the classification and speed up the process, we queried the \textit{WHOIS} records\footnote{\url{https://whois.icann.org}} of every homograph domain name.
+To help with the classification and speed up the process, we queried the \textit{WHOIS} records\endnote{\url{https://whois.icann.org}} of every homograph domain name.
 Some domains had expired at the time of the classification, and were subsequently deleted from the output file.
@@
 
+\theendnotes
+
 \end{document}

### 2017-06-12 docs/paper.tex
Review related work

@@
 \and
-{\rm J. Sidrach\endnotemark[\value{endnote}]}\\
+{\rm J. Sidrach\footnotemark[\value{footnote}]}\\
 \normalfont{\texttt{jsidrach@ucsd.edu}}
@@
 TODO
-- Browsers policy
-- TLDs policy
+- Introduction to the section, two mayor players in preventing the attack, different roles: browsers vs TLDs
+
+\subsection{Browsers}
+TODO
+- Rewrite, browser by browser: chrome, firefox, edge, safari
+- Significant changes in the past years?
+- Not updated browsers/embedded browsers?
+- Screenshot of two actual domains that look the same but are different
+- Cut screenshots better
 
@@
 \begin{figure}[t]
-  \includegraphics[width=\linewidth]{google.png}
-  \includegraphics[width=\linewidth]{fakegoogle.png}
+  \includegraphics[width=\linewidth]{images/google}
+  \includegraphics[width=\linewidth]{images/fakegoogle-punycode}
   \centering
@@
 
-\subsection{Browsers Policy}
 The major browsers have their own IDN policies to defend against IDN homograph attack.
@@
 
-\subsection{TLDs Policy}
+\subsection{Top-Level Domains}
+TODO
+- What does different TLDs do
+- ccTLDs
 
 \section{Related Work}
-TODO
-- Brief analysis of previous papers on the same topic
+Several relevant studies have been conducted to describe the potential security issues with internationalized domain names, while providing possible solutions to mitigate the surface attack of these homograph domain names.
+The first of these studies, \textit{The Homograph Attack}~\cite{gabrilovich2002}, was written by Evgeniy Gabrilovich and Alex Gontmakher in 2001, and proved the feasability of the attack.
 
-Many relevant studies have been conducted to show the vulnerability of IDN and provide possible solution to mitigate IDN homograph attack.
+In 2006, Vicktor Krammer proposed a defense mechanism based on address bar highlighting on the browsers and a better user interface~\cite{krammer2006}.
+This method of defense mainly targets regular users, by making them explicitly aware of the URL differences.
+It checks each character in a URL separately, highlighting digits or characters of various scripts in different background colors, so that users can easily tell the difference.
+It also suggests using larger font sizes in the address bar, to help distinguish possible homograph characters from their Latin counterparts.
 
-In 2001, Evgeniy Gabrilovich and Alex Gontmakher has proved the feasibility of such attack based on the vulnerability of Unicode in \textit{The Homograph Attack}~\cite{theHomoAttack}.
+In 2012, Maurer and H\"{o}fer argued that safe-guards based on browsers' blacklists was far from enough to protect users from sophisticated phishing attacks~\cite{maurer2012}.
+They proposed a more complex method based on URL components and the spell checking functionality of any search engine.
+In this method, a URL is be divided into several parts, namely, base name (the primary domain name as registered at the registrar), sub-domain (part before the primary domain, i.e., before the last identifier and TLD), path domain (sub-folder of the URL), and brand name (any popular brand name that is present in the URL).
+Their algorithm tries to prevent the attack by analyzing each of these URL parts.
+Each one is sent to the search engine for a spelling check, and in the cases that a spelling suggestion is returned, the URL will be marked as suspicious.
+By splitting the URL into these parts, this method aims to cover almost all possible cases of confusable URLs or domain names.
+However, this mechanism relies exclusively on the search engine to return spelling suggestions, and as a result, it is highly dependent on the search engine and query itself.
 
-In 2006, Vicktor Krammer proposed a defense mechanism based on address bar highlighting/indication technique and better UI of the browsers~\cite{phishdefenseKV}.
-His method of defense mainly target at regular users who do not neccessarily have relevant knowledge and through the better rendering of address along with explicit notification or alert on phishing url users would be aware of malicious website.
-This method check each character in an URL separately, highlighting digits or characters of various scripts in different background color so that users will be aware of the difference.
-It also suggest using larger font size in the address bar to help distinguish possible homograph characters from the Latin letter and alerting users when multi-script is detected by means of scripts block\endnote{\url{http://www.unicode.org/reports/tr24/}}.
-His proposal was innovative in his year but not entirely accurate because characters from the same script may be in different blocks while characters from different scripts sometimes lie in the same block.
+While these last two methods were not adopted, they have influenced other possible mitigations currently implemented in most modern browsers.
+For instance, the base name of the URL is displayed in a darker color in Google Chrome and Mozilla Firefox.
+Safari goes a step further and only shows the base name of the URL.
 
-Manurer and Höfer believed that safe guard based on browsers' blacklist is far from enough to protect users from sophisticated phishing attacks~\cite{proc-eds-2012}.
-They proposed an advanced method based on url components and spell checking functionality of search engine.
-In this method, an url would be divided into several subterms, namely, base name\endnote{The primary domain name as registered at the registrar}, subdomain\endnote{A part of the primary domain}, path domain\endnote{A subfolder of the url}, brand name\endnote{A brand name that occurs in a url}.
-Their algorithm is based on the following characteristics on different subterms of url:
-\begin{itemize}
-  \item Base name: Phisher cannot register the original domain but can only register mispelling or homograph domain name because the original one is often registered ahead by the company.
-  \item Subdomain: Phisher can prepend subdomain to the primary domain being attacked to fool users into thinking that they are on the real domain.
-One example would be \url{http://us.battle.net.loginaccoutbattle.net/login/en/login.html}.
-  \item Path domain: Phisher sometimes place a second domain as a subfolder of the url path, usually right after the primary domain name, for instance, \url{http://piasel.altervista.org/www.paypal.com/new/paypal/intl/update}.
-  \item Brand name: There are cases that only the brand name is inserted somewhere in the URL to fool users.
-\end{itemize}
-Each of this components will be sent to search engine as a term for spelling check and in the cases that spelling suggestion is returned the url will be counted as suspicious.
-By splitting a url into these subterms, this method cover almost all possible cases of fake url or domain name.
-However, this mechanism is based on the search engine for return spelling suggestion and as a result, it does not perform well when it is used as sole detection.
+Other attempts to analyze the impact of homograph attacks have also been made.
+In 2009, Peter Hanay and Christopher Bolan~\cite{hannay2009} concluded that, while most modern browsers in fact have implemented useful measures to prevent internationalized domain name homograph attacks, email clients where not nearly as effective, specially when dealing with incoming emails.
+In 2010, Johnny Al Helou and Scott Tilley~\cite{al2010} argued that the introduction of country-code Top Level Domains (ccTLDs) have made this attack easier to perform again.
+
+Our approach to analyze the potential security risk of homograph internationalized domain names was fundamentally different the ones evaluated.
+Rather than inspecting traffic or generating random homograph permutations of a string, we took a more systematic approach.
+We clustered all internationalized homograph domains using a snapshot of the \texttt{.com} domain zone.
+We then used a list of top web sites and domain registrants data to classify each homograph domain name.
 
@@
 One possible explanation for this is that the domain was bought in an attempt to be re-sold later at a higher price to the owner of the matching canonical homograph domain.
+However, the potential security risk is still present as there are no guarantees that the parked domains will remain inactive in the future.
 A detailed breakdown of this classification can be found in Table~\ref{manually-classified-idns}.
@@
 - TLDs
+- Hard to balance (rendering idn useless vs preventing the attack)
 

### 2017-06-13 docs/paper.tex
Made change to background - browser

@@
 
+This section provides some background knowledge for mechanism that defends against internationalized domain name homograph attack.
+There are two mayor players preventing the attack, the browsers and TLDs, with one working on the client side to detect and alert users while the other putting down policies on domain name registerar to restrict the number of possible homographs.
+
 \subsection{Browsers}
@@
 These tests include but not limited to converting to Unicode, less than one numbering systems involved, no invisible characters, etc.
+
 Internet Explorer\endnote{\url{https://support.microsoft.com/en-us/help/17621/internet-explorer-downloads}} displays URLs in IDN form if every component contains only characters from the languages configured in \textit{Internet Options}.
+
 Firefox\endnote{\url{https://www.mozilla.org/en-US/firefox/new/}} uses a script mixing detection algorithm based on \textit{"Moderately Restrictive" profile of Unicode Technical Report 39} and displays Unicode when URL consists of any single script, any single script plus Latin, or it's in the white-list of other combinations.
+
 Opera\endnote{\url{http://www.opera.com}} shows IDN only for whitelisted TLDs.
+
 Safari\endnote{\url{https://www.apple.com/safari}} has a whitelist of scripts that do not contain confusable characters and only shows the IDN form for the whitelisted scripts.

### 2017-06-13 docs/paper.tex
tld

@@
 For example, Google Chrome\endnote{\url{https://www.google.com/chrome}} will display IDN in Unicode only if all characters of the domain names belong to only one language and this language has to be the user's preferred language.
-\ref{screenshot} show the screenshots of the original URL of \url{www.google.com} and its homograph.
+Figure \ref{screenshot} shows the screenshots of the original URL of \url{www.google.com} and its homograph.
 
@@
 - ccTLDs
+
+The Internet Corporation for Assigned Names and Numbers(ICANN) is responsible for the management of domain name system.
+In 2009, ICANN started to accept the application for internationalized country code top-level domain(IDN ccTLD) for the benefits of non-English speaking people and the first IDN ccTLD was added to DNS root zone in 2010\ref{tld1}.
+
+ICANN is aware of the potential vulnerability of homograph attacks and limits the usage of letter that is similar to Latin.
+For any application of potential IDN ccTLD, if there exists letter that is similar to an existing TLD, ICANN may reject them, especially for two-letter TLD.
+Three-letter TLD have higher chance to be accepted, as they are considered to be safer than two-letter TLD.
+ICANN listed detailed checking process in the Final Implementation Plan\ref{icann}.
+
+For the second level domains, some registrant registers similar IDNs for brand protection, like Google. Google has registered most IDN in 2005.
 

### 2017-06-13 docs/paper.tex
Change updat\e

--- 2017-06-13 docs/paper.tex
@@
 \begin{figure}[t]
-  \includegraphics[width=\linewidth]{images/google}
-  \includegraphics[width=\linewidth]{images/fakegoogle-punycode}
+  \includegraphics[width=\linewidth]{images/apple}
+  \includegraphics[width=\linewidth]{images/fakeapple-punycode}
   \centering
-  \caption{Google(top) and its homograph(bottom) on Chrome}
+  \caption{Apple official website(top) and its homograph(bottom) on Chrome}
   \label{screenshot}
@@
 The major browsers have their own IDN policies to defend against IDN homograph attack.
-Google Chrome, starting with Chrome 51, will display Punycode if certain tests fail on the input URL.
+
+Google Chrome, starting with Chrome 51, used to display Punycode if certain tests fail on the input URL.
 These tests include but not limited to converting to Unicode, less than one numbering systems involved, no invisible characters, etc.
+However, Chrome displayed IDNs that consist purely of cyrillic characters normally, which allow IDN homograph attack of this kind.
+Starting from version 59, Chrome checks cryl-latin alikes characters only for non-IDN TLDs and block a label made entirely of Latin-look-alike Cryllic letters for non-IDN TLDs.
+
+Firefox\endnote{\url{https://www.mozilla.org/en-US/firefox/new/}} used to adopt a long whitelist and only display as Unicode all IDN labels within TLDs on it.
+Currently, the browser uses a script mixing detection algorithm based on \textit{"Moderately Restrictive" profile of Unicode Technical Report 39} and displays Unicode when URL consists of any single script, any single script plus Latin, or it's in the white-list of other combinations.
+As for domain names made entirely of Cryllic letters, Firefox leave this issue to registries to make sure that their customers cannot rip each other off\footnote{\url{https://wiki.mozilla.org/IDN_Display_Algorithm}}.
 
 Internet Explorer\endnote{\url{https://support.microsoft.com/en-us/help/17621/internet-explorer-downloads}} displays URLs in IDN form if every component contains only characters from the languages configured in \textit{Internet Options}.
-
-Firefox\endnote{\url{https://www.mozilla.org/en-US/firefox/new/}} uses a script mixing detection algorithm based on \textit{"Moderately Restrictive" profile of Unicode Technical Report 39} and displays Unicode when URL consists of any single script, any single script plus Latin, or it's in the white-list of other combinations.
-
-Opera\endnote{\url{http://www.opera.com}} shows IDN only for whitelisted TLDs.
+%Edge should probably do the same
 

### 2017-06-14 docs/paper.tex
Add usenix, review abstract and browsers

--- 2017-06-13 docs/paper.tex
@@
 \documentclass[letterpaper,twocolumn,10pt]{article}
-\usepackage{url,epsfig,endnotes}
+\usepackage{usenix,url,epsfig,endnotes}
 \providecommand{\keywords}[1]{\textbf{\textit{Keywords:}} #1}
@@
 \author{
-{\rm Chen Lai\footnote{Author names are ordered lexicographically, by last name.}}\\
+{\rm Chen Lai\thanks{Author names are ordered lexicographically, by last name.}}\\
 \normalfont{\texttt{chl588@ucsd.edu}}
 \and
-{\rm Zhongrong Jian\footnotemark[\value{footnote}]}\\
+{\rm Zhongrong Jian\footnotemark[1]}\\
 \normalfont{\texttt{zhjian@ucsd.edu}}
 \and
-{\rm J. Sidrach\footnotemark[\value{footnote}]}\\
+{\rm J. Sidrach\footnotemark[1]}\\
 \normalfont{\texttt{jsidrach@ucsd.edu}}
@@
 \abstract{
-The invention of Unicode made it possible for non-English speaking people to enter the world of Internet.
-However, it also open up the possibilities of malicious use of URL.
-Sometimes different letters from different languages can look almost the same depending on the font.
-This paper mainly summarize the previous relevant work and analyze the current circumstance of Internationalized Domain Name Homograph Attack on the Internet via statistical approach on the websites from Alexa top 1 million rankings.
-Through the analysis results we will be able to provide some insight on this subject.
+The introduction of Internationalized Domain Names made access the web easier to non-English speakers.
+However, it also opened the possibility of using homograph domain names maliciously.
+We analyzed the potential impact of this type of attack, commonly referred to as IDN homograph attack.
+Our approach was based on clustering internationalized domain names with their counterparts in the Alexa Top 1m web sites ranking.
+The results obtained indicate that there are more than a thousand (at least) IDN homographs among \textit{.com} domains.
+Most of them are not being used actively, but they still posses a potential security risk as there are no guarantees they will remain inactive in the future.
 }
@@
 Domain names were originally designed to only support ASCII characters.
-Internationalized Domain Names (IDNs) were proposed back in December 1996 by Martin D\"{u}rst\endnote{\url{https://tools.ietf.org/html/draft-duerst-dns-i18n-00}} for the purpose of letting non-English speaking people use Internet without additional restrictions.
+Internationalized Domain Names (IDNs) were proposed back in December 1996 by Martin D\"{u}rst\endnote{\url{https://tools.ietf.org/html/draft-duerst-dns-i18n-00}} for the purpose of letting non-English speakers use Internet without additional restrictions.
 This extension involves representing Unicode characters in ASCII using Punycode, so that they could be then rendered back into their Unicode representation.
@@
 
-In this paper, we analyze the potential impact of this type of attack, commonly referred to as IDN Homograph Attack.
+In this paper, we analyze the potential impact of this type of attack, commonly referred to as IDN homograph attack.
 Section 2 explains past and present policies of major browsers and top-level domain (TLD) registrants in an attempt to prevent the attack.
@@
 \section{Background}
-TODO
-- Introduction to the section, two mayor players in preventing the attack, different roles: browsers vs TLDs
-
-This section provides some background knowledge for mechanism that defends against internationalized domain name homograph attack.
-There are two mayor players preventing the attack, the browsers and TLDs, with one working on the client side to detect and alert users while the other putting down policies on domain name registerar to restrict the number of possible homographs.
+This section summarizes different mechanisms used to defend against internationalized domain name homograph attack.
+There are two mayor players trying to prevent this kind of attack, browsers and TLDs.
+Browsers, on the client side, display the non-Unicode version of the domain name based on different white-lists and restrictions.
+TLDs, on the other side, have different policies on domain name registrations to try to restrict the use of homographs.
+A more comprehensive study would be required for other possible attack vectors, such as email clients.
 
 \subsection{Browsers}
-TODO
-- Rewrite, browser by browser: chrome, firefox, edge, safari
-- Significant changes in the past years?
-- Not updated browsers/embedded browsers?
-- Screenshot of two actual domains that look the same but are different
-- Cut screenshots better
-
-Currently, most popular browsers will show the host name in Unicode depends on the language setting to defend IDN attack.
-For example, Google Chrome\endnote{\url{https://www.google.com/chrome}} will display IDN in Unicode only if all characters of the domain names belong to only one language and this language has to be the user's preferred language.
-Figure \ref{screenshot} shows the screenshots of the original URL of \url{www.google.com} and its homograph.
+\begin{figure}[t]
+  \includegraphics[width=\linewidth]{images/apple}
+  \includegraphics[width=\linewidth]{images/fakeapple-punycode}
+  \centering
+  \caption{Apple's official website (top) and its IDN homograph (bottom), as displayed on Chrome 55.}
+  \label{screenshot-apple}
+\end{figure}
 
@@
   \centering
-  \caption{Google(top) and its homograph(bottom) on Chrome}
-  \label{screenshot}
+  \caption{Google's official website (top) and its IDN homograph (bottom), as displayed on Chrome 55.}
+  \label{screenshot-google}
 \end{figure}
 
-The major browsers have their own IDN policies to defend against IDN homograph attack.
-Google Chrome, starting with Chrome 51, will display Punycode if certain tests fail on the input URL.
-These tests include but not limited to converting to Unicode, less than one numbering systems involved, no invisible characters, etc.
+All major browsers display the URL in Punycode instead of Unicode if certain conditions are met, to defend the user against a possible IDN homograph attack.
+The specific conditions, however, are different for each browser.
+Figure~\ref{screenshot-apple} shows a successful attack where the homograph domain name was not detected.
+Figure~\ref{screenshot-google} show an unsuccessful attack, where the URL is displayed in Punycode.
 
-Internet Explorer\endnote{\url{https://support.microsoft.com/en-us/help/17621/internet-explorer-downloads}} displays URLs in IDN form if every component contains only characters from the languages configured in \textit{Internet Options}.
-
-Firefox\endnote{\url{https://www.mozilla.org/en-US/firefox/new/}} uses a script mixing detection algorithm based on \textit{"Moderately Restrictive" profile of Unicode Technical Report 39} and displays Unicode when URL consists of any single script, any single script plus Latin, or it's in the white-list of other combinations.
-
-Opera\endnote{\url{http://www.opera.com}} shows IDN only for whitelisted TLDs.
-
-Safari\endnote{\url{https://www.apple.com/safari}} has a whitelist of scripts that do not contain confusable characters and only shows the IDN form for the whitelisted scripts.
+Firefox (version 54 at the time of writing) uses a script mixing detection algorithm based on the ``Moderately Restrictive'' profile defined in the \textit{Unicode Technical Standard \#39}\endnote{\url{http://www.unicode.org/reports/tr39}}.
+It displays the URL in Unicode when all characters belong to a single script, to a single script plus Latin, or to a the white-list of other combinations.
+Google Chrome (version 59 at the time of writing), among other things, checks Latin-look-alike Cyrillic characters in non-IDN TLDs.
+This change was introduced recently, after a proof-of-concept IDN homograph attack working on Chrome was submitted to their issue tracker\endnote{\url{https://bugs.chromium.org/p/chromium/issues/detail?id=683314}}.
+Internet Explorer and Edge (version 11 and 40 at the of writing, respectively) display the URL in Unicode if every component of the URL contains only characters from the languages configured in the operating system's \textit{Internet Options}.
+Safari (version 10 at the time of writing) has a white-list of scripts that do not contain confusable characters, and only shows the URL in Unicode for those white-listed scripts.
 
@@
 The detection of homograph domain names was done using an algorithm to check if two strings are confusable.
-This algorithm is described in the \textit{Unicode Technical Standard \#39}\endnote{\url{http://www.unicode.org/reports/tr39}}.
+This algorithm is described in the \textit{Unicode Technical Standard \#39}.
 The approach followed has some caveats, that could be addressed in future work.
@@
 
-\section{Results}
+% TODO: Align tables
 
-\begin{table*}[ht!]
+\begin{table*}[]
 \centering
@@
 
-We obtained 458731 domain names from the \textit{top domains snapshot} that belonged to the \texttt{.com} zone.
-From the \textit{.com snapshot}, we identified a total of 1044301 internationalized domains.
-However, only a low percentage of the internationalized domain names (3.68\%) had a matching homograph canonical domain name in the \textit{top domains snapshot}.
-Even if we take into account that our homograph detection algorithm is rather limited (as described before), these results still indicate that the majority of internationalized domain names are not being used in homograph attacks.
-An overview of these clustering results can be found in Table~\ref{clustering-results}.
-
-Table~\ref{top-com-alexa-with-idns} shows the number of internationalized domain name homographs for the top ten \texttt{.com} domains.
-It is worth noting that most of the homograph domains of \textit{google.com} are actually registered by Google, possibly as a defensive measure.
-Another surprising result of the homograph clustering is that 81.87\% of the groups have just one homograph internationalized domain name.
-This suggests that this kind of attack may not be targeted only to top websites, but rather to any domain where valuable information could be obtained from the users by a scam.
-
-\begin{table}[ht!]
+\begin{table}[]
 \centering
@@
 
-The manual classification sheds some light on how these homograph internationalized domain names are currently being used.
-For the most part (82.34\%), the domains are registered by a third party, and not being used actively (parking).
-One possible explanation for this is that the domain was bought in an attempt to be re-sold later at a higher price to the owner of the matching canonical homograph domain.
-However, the potential security risk is still present as there are no guarantees that the parked domains will remain inactive in the future.
-A detailed breakdown of this classification can be found in Table~\ref{manually-classified-idns}.
-
-\begin{table}[ht!]
+\begin{table}[]
 \centering
@@
 
-Table~\ref{top-registrants-homograph-idns} contains the top ten registrants with the most homograph internationalized domain names.
-Most of these registrants are actually domain privacy companies, so it is impossible to know if the domains belong to the same person or not.
-There are also several individuals with a high number of homograph internationalized domain names.
-It is also worth mentioning that some of these individuals seem to be targeting specific industries.
-For instance, a single person has registered homographs of ``audi'', ``citroen'' and ``diesel''.
-
-\begin{table*}[ht!]
+\begin{table*}[]
 \centering
@@
 \end{table*}
+
+\section{Results}
+
+We obtained 458731 domain names from the \textit{top domains snapshot} that belonged to the \texttt{.com} zone.
+From the \textit{.com snapshot}, we identified a total of 1044301 internationalized domains.
+However, only a low percentage of the internationalized domain names (3.68\%) had a matching homograph canonical domain name in the \textit{top domains snapshot}.
+Even if we take into account that our homograph detection algorithm is rather limited (as described before), these results still indicate that the majority of internationalized domain names are not being used in homograph attacks.
+An overview of these clustering results can be found in Table~\ref{clustering-results}.
+
+Table~\ref{top-com-alexa-with-idns} shows the number of internationalized domain name homographs for the top ten \texttt{.com} domains.
+It is worth noting that most of the homograph domains of \textit{google.com} are actually registered by Google, possibly as a defensive measure.
+Another surprising result of the homograph clustering is that 81.87\% of the groups have just one homograph internationalized domain name.
+This suggests that this kind of attack may not be targeted only to top websites, but rather to any domain where valuable information could be obtained from the users by a scam.
+
+The manual classification sheds some light on how these homograph internationalized domain names are currently being used.
+For the most part (82.34\%), the domains are registered by a third party, and not being used actively (parking).
+One possible explanation for this is that the domain was bought in an attempt to be re-sold later at a higher price to the owner of the matching canonical homograph domain.
+However, the potential security risk is still present as there are no guarantees that the parked domains will remain inactive in the future.
+A detailed breakdown of this classification can be found in Table~\ref{manually-classified-idns}.
+
+Table~\ref{top-registrants-homograph-idns} contains the top ten registrants with the most homograph internationalized domain names.
+Most of these registrants are actually domain privacy companies, so it is impossible to know if the domains belong to the same person or not.
+There are also several individuals with a high number of homograph internationalized domain names.
+It is also worth mentioning that some of these individuals seem to be targeting specific industries.
+For instance, a single person has registered homographs of ``audi'', ``citroen'' and ``diesel''.
 

### 2017-06-14 docs/paper.tex
Typo
add tld

--- 2017-06-13 docs/paper.tex
@@
 \begin{figure}[t]
-  \includegraphics[width=\linewidth]{images/apple}
-  \includegraphics[width=\linewidth]{images/fakeapple-punycode}
+  \includegraphics[width=\linewidth]{images/google}
+  \includegraphics[width=\linewidth]{images/fakegoogle-punycode}
   \centering
-  \caption{Apple official website(top) and its homograph(bottom) on Chrome}
+  \caption{Google(top) and its homograph(bottom) on Chrome}
   \label{screenshot}
@@
 The major browsers have their own IDN policies to defend against IDN homograph attack.
-
-Google Chrome, starting with Chrome 51, used to display Punycode if certain tests fail on the input URL.
+Google Chrome, starting with Chrome 51, will display Punycode if certain tests fail on the input URL.
 These tests include but not limited to converting to Unicode, less than one numbering systems involved, no invisible characters, etc.
-However, Chrome displayed IDNs that consist purely of cyrillic characters normally, which allow IDN homograph attack of this kind.
-Starting from version 59, Chrome checks cryl-latin alikes characters only for non-IDN TLDs and block a label made entirely of Latin-look-alike Cryllic letters for non-IDN TLDs.
-
-Firefox\endnote{\url{https://www.mozilla.org/en-US/firefox/new/}} used to adopt a long whitelist and only display as Unicode all IDN labels within TLDs on it.
-Currently, the browser uses a script mixing detection algorithm based on \textit{"Moderately Restrictive" profile of Unicode Technical Report 39} and displays Unicode when URL consists of any single script, any single script plus Latin, or it's in the white-list of other combinations.
-As for domain names made entirely of Cryllic letters, Firefox leave this issue to registries to make sure that their customers cannot rip each other off\footnote{\url{https://wiki.mozilla.org/IDN_Display_Algorithm}}.
 
 Internet Explorer\endnote{\url{https://support.microsoft.com/en-us/help/17621/internet-explorer-downloads}} displays URLs in IDN form if every component contains only characters from the languages configured in \textit{Internet Options}.
-%Edge should probably do the same
+
+Firefox\endnote{\url{https://www.mozilla.org/en-US/firefox/new/}} uses a script mixing detection algorithm based on \textit{"Moderately Restrictive" profile of Unicode Technical Report 39} and displays Unicode when URL consists of any single script, any single script plus Latin, or it's in the white-list of other combinations.
+
+Opera\endnote{\url{http://www.opera.com}} shows IDN only for whitelisted TLDs.
 
@@
 
-The Internet Corporation for Assigned Names and Numbers(ICANN) is responsible for the management of domain name system.
+The Internet Corporation for Assigned Names and Numbers(ICANN) is an organization responsible for the management of domain name system.
 In 2009, ICANN started to accept the application for internationalized country code top-level domain(IDN ccTLD) for the benefits of non-English speaking people and the first IDN ccTLD was added to DNS root zone in 2010\ref{tld1}.
@@
 ICANN listed detailed checking process in the Final Implementation Plan\ref{icann}.
+
+Although the vulnerability of homograph has been introduced as early as 2001, most registrant of TLD don't have the policy to defend homograph attack.
+Only several TLD have published policy to eliminate the potential risk of specific language.
+For example, .cn .biz, .hk, and all Chinese TLD will activate both traditional Chinese domain and simplified Chinese domain once one of it is registered.
+Registering with characters in both traditional Chinese and simplified Chinese is not allowed.
+
+- TODO it was found in wiki, but i didn't find source document.
+(In .org domain, once one letter is used in the domain, other homograph letters corresponding to the same domain will be prohibited.)
 

### 2017-06-14 docs/paper.tex

--- 2017-06-14 docs/paper.tex
@@
 This section summarizes different mechanisms used to defend against internationalized domain name homograph attack.
-There are two mayor players trying to prevent this kind of attack, browsers and TLDs.
+There are two major players trying to prevent this kind of attack, browsers and TLDs.
 Browsers, on the client side, display the non-Unicode version of the domain name based on different white-lists and restrictions.

### 2017-06-14 docs/paper.tex
Draft of everything except Conclusions

--- 2017-06-14 docs/paper.tex
@@
 \documentclass[letterpaper,twocolumn,10pt]{article}
-\usepackage{usenix,url,epsfig,endnotes}
+\usepackage{usenix,url,epsfig,endnotes,dblfloatfix}
 \providecommand{\keywords}[1]{\textbf{\textit{Keywords:}} #1}
@@
 The results obtained indicate that there are more than a thousand (at least) IDN homographs among \textit{.com} domains.
-Most of them are not being used actively, but they still posses a potential security risk as there are no guarantees they will remain inactive in the future.
+While most of them are not being used actively, they still possess a potential security risk as there are no guarantees they will remain inactive in the future.
 }
@@
 For example, Cyrillic letter ``a'' can look identical to Latin letter ``a'' depending on the font.
-In other languages, like Chinese, there exists many homograph letters between traditional Chinese and simplified Chinese.
+In other languages, like Chinese, there exist many homograph letters between traditional Chinese and simplified Chinese.
 Malicious attackers could then register a domain where one of the letters is actually Cyrillic but whose representation matched a Latin one.
@@
 
-\subsection{Top-Level Domains}
-TODO
-- What does different TLDs do
-- ccTLDs
+\subsection{ICANN and TLD Registrars}
+The Internet Corporation for Assigned Names and Numbers (ICANN) is the organization responsible for the management of domain name system.
+In 2009, ICANN started to accept applications for internationalized country code top-level domains (IDN ccTLDs).
+The first IDN ccTLD was added to DNS root zone in 2010~\cite{mac2010}.
+ICANN is aware of the potential security risk that homograph attacks pose, and limits the usage of Latin-look-alike letters.
+They may reject applications for IDN ccTLDs if there exists an existing TLD that looks similar to the one being petitioned for.
+The detailed checking process is defined in their ``Final Implementation Plan for IDN ccTLD Fast Track Process''~\cite{icann2013}.
 
-The Internet Corporation for Assigned Names and Numbers(ICANN) is responsible for the management of domain name system.
-In 2009, ICANN started to accept the application for internationalized country code top-level domain(IDN ccTLD) for the benefits of non-English speaking people and the first IDN ccTLD was added to DNS root zone in 2010\ref{tld1}.
-
-ICANN is aware of the potential vulnerability of homograph attacks and limits the usage of letter that is similar to Latin.
-For any application of potential IDN ccTLD, if there exists letter that is similar to an existing TLD, ICANN may reject them, especially for two-letter TLD.
-Three-letter TLD have higher chance to be accepted, as they are considered to be safer than two-letter TLD.
-ICANN listed detailed checking process in the Final Implementation Plan\ref{icann}.
-
-For the second level domains, some registrant registers similar IDNs for brand protection, like Google. Google has registered most IDN in 2005.
+Most second level registrars do not have a explicit public policy to prevent the registration of homograph domains.
+Only a few have implemented restrictions to eliminate this potential risk.
+For instance, \texttt{.cn}, \texttt{.biz}, \texttt{.hk}, and all Chinese TLDs will simultaneously activate both traditional and simplified Chinese IDNs once one of them is registered.
 
@@
 
-\subsection{Manual Classification}
-The last part of the data processing was the classification of the homograph domain names.
-This classification was done manually, to be able to differentiate between scam and unrelated websites.
-To help with the classification and speed up the process, we queried the \textit{WHOIS} records\endnote{\url{https://whois.icann.org}} of every homograph domain name.
-Some domains had expired at the time of the classification, and were subsequently deleted from the output file.
-
-The two high level categories that were defined are \textit{Canonical} and \textit{Third Party}.
-The first one, \textit{Canonical}, was employed when the domain is registered by the same organization as its canonical homograph domain name.
-The second one, \textit{Third Party}, was used when the domain is registered by a different organization than its canonical homograph domain name.
-Additionally, a more detailed classification was made:
-\itemize{
-\setlength{\itemsep}{0pt}
-\setlength{\parskip}{0pt}
-\setlength{\parsep}{0pt}
-\item \textit{Canonical - Parking}: domain was registered but it was not accessible via HTTP.
-\item \textit{Canonical - Redirect}: domain redirected (HTTP Status Code 301/307/308) to its canonical homograph domain name.
-\item \textit{Third Party - Redirect to Canonical:} domain redirected (HTTP Status Code 301/307/308) to its canonical homograph domain name.
-\item \textit{Third Party - Unrelated}: domain resolved, but the contents of the website were totally unrelated to its canonical homograph domain name.
-\item \textit{Third Party - Parking}: domain was registered, but it was not accessible via HTTP, or when accessed, a default domain parking web page was displayed.
-\item \textit{Third Party - Scam}: domain resolved, and the website displayed was a clear attempt (similar color, logos, etc.) to make users think they were visiting the canonical homograph domain name.
-}
-
-% TODO: Align tables
-
-\begin{table*}[]
+\begin{table*}[b!]
 \centering
@@
 
-\begin{table}[]
+\subsection{Manual Classification}
+The last part of the data processing was the classification of the homograph domain names.
+This classification was done manually, to be able to differentiate between scam and unrelated websites.
+To help with the classification and speed up the process, we queried the \textit{WHOIS} records\endnote{\url{https://whois.icann.org}} of every homograph domain name.
+Some domains had expired at the time of the classification, and were subsequently deleted from the output file.
+
+The two high level categories that were defined are \textit{Canonical} and \textit{Third Party}.
+The first one, \textit{Canonical}, was employed when the domain is registered by the same organization as its canonical homograph domain name.
+The second one, \textit{Third Party}, was used when the domain is registered by a different organization than its canonical homograph domain name.
+Additionally, a more detailed classification was made:
+\begin{itemize}
+\setlength{\itemsep}{0pt}
+\setlength{\parskip}{0pt}
+\setlength{\parsep}{0pt}
+\item \textit{Canonical - Parking}: domain was registered but it was not accessible via HTTP.
+\item \textit{Canonical - Redirect}: domain redirected (HTTP Status Code 301/307/308) to its canonical homograph domain name.
+\item \textit{Third Party - Redirect to Canonical:} domain redirected (HTTP Status Code 301/307/308) to its canonical homograph domain name.
+\item \textit{Third Party - Unrelated}: domain resolved, but the contents of the website were totally unrelated to its canonical homograph domain name.
+\item \textit{Third Party - Parking}: domain was registered, but it was not accessible via HTTP, or when accessed, a default domain parking web page was displayed.
+\item \textit{Third Party - Scam}: domain resolved, and the website displayed was a clear attempt (similar color, logos, etc.) to make users think they were visiting the canonical homograph domain name.
+\end{itemize}
+
+\section{Results}
+We obtained 458731 domain names from the \textit{top domains snapshot} that belonged to the \texttt{.com} zone.
+From the \textit{.com snapshot}, we identified a total of 1044301 internationalized domains.
+However, only a low percentage of the internationalized domain names (3.68\%) had a matching homograph canonical domain name in the \textit{top domains snapshot}.
+Even if we take into account that our homograph detection algorithm is rather limited (as described before), these results still indicate that the majority of internationalized domain names are not being used in homograph attacks.
+An overview of these clustering results can be found in Table~\ref{clustering-results}.
+
+\begin{table}[!ht]
 \centering
@@
 
-\section{Results}
-
-We obtained 458731 domain names from the \textit{top domains snapshot} that belonged to the \texttt{.com} zone.
-From the \textit{.com snapshot}, we identified a total of 1044301 internationalized domains.
-However, only a low percentage of the internationalized domain names (3.68\%) had a matching homograph canonical domain name in the \textit{top domains snapshot}.
-Even if we take into account that our homograph detection algorithm is rather limited (as described before), these results still indicate that the majority of internationalized domain names are not being used in homograph attacks.
-An overview of these clustering results can be found in Table~\ref{clustering-results}.
-
 Table~\ref{top-com-alexa-with-idns} shows the number of internationalized domain name homographs for the top ten \texttt{.com} domains.
@@
 Another surprising result of the homograph clustering is that 81.87\% of the groups have just one homograph internationalized domain name.
-This suggests that this kind of attack may not be targeted only to top websites, but rather to any domain where valuable information could be obtained from the users by a scam.
+This suggests that this kind of attack may not be targeted only to top websites, but rather to any domain where valuable information could be scammed from users.
 
@@
 
+\clearpage
+
 {\footnotesize \bibliographystyle{acm}

### 2017-06-14 docs/paper.tex
Abstract reviewed

@@
 \abstract{
-The introduction of Internationalized Domain Names made access the web easier to non-English speakers.
-However, it also opened the possibility of using homograph domain names maliciously.
-We analyzed the potential impact of this type of attack, commonly referred to as IDN homograph attack.
-Our approach was based on clustering internationalized domain names with their counterparts in the Alexa Top 1m web sites ranking.
+The introduction of Internationalized Domain Names (IDNs) made access the web easier to non-English speakers.
+However, it also opened up the possibility of using homograph domain names maliciously, in what has been called IDN homograph attacks.
+This kind of attack can be used to trick users into thinking they are visiting a different (but homograph) domain name.
+Our approach to analyze its potential impact was based on clustering internationalized domain names with their counterparts in the Alexa Top 1m web sites ranking.
 The results obtained indicate that there are more than a thousand (at least) IDN homographs among \textit{.com} domains.

### 2017-06-14 docs/paper.tex
IDNs

@@
 This kind of attack can be used to trick users into thinking they are visiting a different (but homograph) domain name.
-Our approach to analyze its potential impact was based on clustering internationalized domain names with their counterparts in the Alexa Top 1m web sites ranking.
+Our approach to analyze its potential impact was based on clustering IDNs with their canonical counterparts in the Alexa Top 1m web sites ranking.
 The results obtained indicate that there are more than a thousand (at least) IDN homographs among \textit{.com} domains.
@@
 Domain names were originally designed to only support ASCII characters.
-Internationalized Domain Names (IDNs) were proposed back in December 1996 by Martin D\"{u}rst\endnote{\url{https://tools.ietf.org/html/draft-duerst-dns-i18n-00}} for the purpose of letting non-English speakers use Internet without additional restrictions.
+IDNs were proposed back in December 1996 by Martin D\"{u}rst\endnote{\url{https://tools.ietf.org/html/draft-duerst-dns-i18n-00}} for the purpose of letting non-English speakers use Internet without additional restrictions.
 This extension involves representing Unicode characters in ASCII using Punycode, so that they could be then rendered back into their Unicode representation.
@@
 In this paper, we analyze the potential impact of this type of attack, commonly referred to as IDN homograph attack.
-Section 2 explains past and present policies of major browsers and top-level domain (TLD) registrants in an attempt to prevent the attack.
+Section 2 explains past and present policies of major browsers and domain registrars in an attempt to prevent the attack.
 Section 3 explores relevant work in the literature related to homograph attacks.
@@
 \section{Related Work}
-Several relevant studies have been conducted to describe the potential security issues with internationalized domain names, while providing possible solutions to mitigate the surface attack of these homograph domain names.
+Several relevant studies have been conducted to describe the potential security issues with IDNs, while providing possible solutions to mitigate the surface attack of these homograph domain names.
 The first of these studies, \textit{The Homograph Attack}~\cite{gabrilovich2002}, was written by Evgeniy Gabrilovich and Alex Gontmakher in 2001, and proved the feasability of the attack.
@@
 In 2009, Peter Hanay and Christopher Bolan~\cite{hannay2009} concluded that, while most modern browsers in fact have implemented useful measures to prevent internationalized domain name homograph attacks, email clients where not nearly as effective, specially when dealing with incoming emails.
-In 2010, Johnny Al Helou and Scott Tilley~\cite{al2010} argued that the introduction of country-code Top Level Domains (ccTLDs) have made this attack easier to perform again.
+In 2010, Johnny Al Helou and Scott Tilley~\cite{al2010} argued that the introduction of ccTLDs have made this attack easier to perform again.
 
-Our approach to analyze the potential security risk of homograph internationalized domain names was fundamentally different the ones evaluated.
+Our approach to analyze the potential security risk of homograph IDNs was fundamentally different the ones evaluated.
 Rather than inspecting traffic or generating random homograph permutations of a string, we took a more systematic approach.
@@
 We used the \textit{.com snapshot} to obtain all the internationalized domains of the \texttt{.com} domain zone.
-All internationalized domain names are represented using Punycode, so they start with the \texttt{xn--} prefix.
+All IDNs are represented using Punycode, so they start with the \texttt{xn--} prefix.
 Using this information we first filtered the \textit{.com snapshot} to match only the \texttt{.com} domains that start with \texttt{xn--}.
@@
 We used the \textit{top domains snapshot} as a source for the canonical (non-international) domain name of a website, based on its ranking.
-As we were only interested in non-internationalized domain names, we discarded the ones that start with the prefix \texttt{xn--}.
-We also removed sub-domains, since we only had top-level domain names in the \textit{.com snapshot}.
+As we were only interested in non-IDNs, we discarded the ones that start with the prefix \texttt{xn--}.
+We also removed sub-domains, since we only had second level domain names in the \textit{.com snapshot}.
 
@@
 The underlying assumptions behind the clustering process are that homograph attacks are more likely to target popular domains, and that the million domains from the \textit{top domains snapshot} contains most of the popular domains.
-To detect potential internationalized domain name homograph attacks, we clustered the internationalized domain names in the \textit{.com snapshot}.
+To detect potential internationalized domain name homograph attacks, we clustered the IDNs in the \textit{.com snapshot}.
 The representative of each cluster is a homograph domain name from the \textit{top domains snapshot}, which we called canonical domain name.
@@
 \hspace{0.5cm} Without IDN homographs             & 457906                     & 2.27\%                     \\
-\itshape\sffamily{Internationalized Domain Names} & \itshape\sffamily{1045400} & \itshape\sffamily{91.69\%} \\
+\itshape\sffamily{IDNs} & \itshape\sffamily{1045400} & \itshape\sffamily{91.69\%} \\
 \hspace{0.5cm} With canonical homograph           & 1099                       & 3.68\%                     \\
@@
 From the \textit{.com snapshot}, we identified a total of 1044301 internationalized domains.
-However, only a low percentage of the internationalized domain names (3.68\%) had a matching homograph canonical domain name in the \textit{top domains snapshot}.
-Even if we take into account that our homograph detection algorithm is rather limited (as described before), these results still indicate that the majority of internationalized domain names are not being used in homograph attacks.
+However, only a low percentage of the IDNs (3.68\%) had a matching homograph canonical domain name in the \textit{top domains snapshot}.
+Even if we take into account that our homograph detection algorithm is rather limited (as described before), these results still indicate that the majority of IDNs are not being used in homograph attacks.
 An overview of these clustering results can be found in Table~\ref{clustering-results}.
@@
 
-The manual classification sheds some light on how these homograph internationalized domain names are currently being used.
+The manual classification sheds some light on how these homograph IDNs are currently being used.
 For the most part (82.34\%), the domains are registered by a third party, and not being used actively (parking).
@@
 
-Table~\ref{top-registrants-homograph-idns} contains the top ten registrants with the most homograph internationalized domain names.
+Table~\ref{top-registrants-homograph-idns} contains the top ten registrants with the most homograph IDNs.
 Most of these registrants are actually domain privacy companies, so it is impossible to know if the domains belong to the same person or not.
-There are also several individuals with a high number of homograph internationalized domain names.
+There are also several individuals with a high number of homograph IDNs.
 It is also worth mentioning that some of these individuals seem to be targeting specific industries.
@@
 The full \texttt{.com} domain zone snapshot will not be publicly disclosed, as its access requires a paid subscription.
-The retrieval of the \textit{WHOIS} information was performed only for the homograph internationalized domain names, which were about one thousand.
+The retrieval of the \textit{WHOIS} information was performed only for the homograph IDNs, which were about one thousand.
 It was performed with a significant delay between petitions (3 seconds) in order to avoid saturating the servers.
@@
 
-\clearpage
-
 {\footnotesize \bibliographystyle{acm}

### 2017-06-14 docs/paper.tex
Conclusions

@@
 ICANN is aware of the potential security risk that homograph attacks pose, and limits the usage of Latin-look-alike letters.
-They may reject applications for IDN ccTLDs if there exists an existing TLD that looks similar to the one being petitioned for.
+They may reject applications for IDN ccTLDs if there already exists a TLD that looks similar to the one being petitioned for.
 The detailed checking process is defined in their ``Final Implementation Plan for IDN ccTLD Fast Track Process''~\cite{icann2013}.
 
-Most second level registrars do not have a explicit public policy to prevent the registration of homograph domains.
+Most second level registrars do not have an explicit public policy to prevent the registration of homograph domains.
 Only a few have implemented restrictions to eliminate this potential risk.
@@
 \hspace{0.5cm} Without IDN homographs             & 457906                     & 2.27\%                     \\
-\itshape\sffamily{IDNs} & \itshape\sffamily{1045400} & \itshape\sffamily{91.69\%} \\
+\itshape\sffamily{Internationalized Domain Names} & \itshape\sffamily{1045400} & \itshape\sffamily{91.69\%} \\
 \hspace{0.5cm} With canonical homograph           & 1099                       & 3.68\%                     \\
@@
 \section{Conclusions}
-TODO
-- Conclusions of our work
-- Possible future work
-- TLDs
-- Hard to balance (rendering idn useless vs preventing the attack)
+We provide a systematic method to evaluate the potential threat that IDN homographs present.
+Our data shows that there are more than a thousand IDN homographs in the \textit{.com} zone.
+Even if the vast majority these are parking domains, there are no guarantees that they will remain inactive in the future.
+Surprisingly, most TLDs do not have common policies to prevent the registration of homograph domains.
+
+It is also important to remember that while the easiest solution would be displaying always URLs in Punycode instead of Unicode, that would completely defeat the purpose of IDNs.
+Browsers have to balance user experience and security.
+They need to allow users to type, navigate and see domains in their language of choice; while at the same time they should avoid misleading users into thinking they are in a legitimate domain when they are not.
+
+Regarding future work, the next logical steps would be to repeat this analysis in other TLDs, and to improve the homograph matching algorithm.
+A more challenging enchancement would be to perform the classification of homograph IDNs without manual intervention by analyzing \textit{WHOIS} records and the \textit{HTTP/HTML} responses.
 

### 2017-06-14 docs/paper.tex
Fix typo

@@
 Regarding future work, the next logical steps would be to repeat this analysis in other TLDs, and to improve the homograph matching algorithm.
-A more challenging enchancement would be to perform the classification of homograph IDNs without manual intervention by analyzing \textit{WHOIS} records and the \textit{HTTP/HTML} responses.
+A more challenging enhancement would be to perform the classification of homograph IDNs without manual intervention by analyzing \textit{WHOIS} records and the \textit{HTTP/HTML} responses.
 

### 2017-06-14 docs/paper.tex
Global revision

@@
 Our approach to analyze its potential impact was based on clustering IDNs with their canonical counterparts in the Alexa Top 1m web sites ranking.
-The results obtained indicate that there are more than a thousand (at least) IDN homographs among \textit{.com} domains.
+The results obtained indicate that there are more than a thousand IDN homographs among \textit{.com} domains.
 While most of them are not being used actively, they still possess a potential security risk as there are no guarantees they will remain inactive in the future.
@@
 
-Firefox (version 54 at the time of writing) uses a script mixing detection algorithm based on the ``Moderately Restrictive'' profile defined in the \textit{Unicode Technical Standard \#39}\endnote{\url{http://www.unicode.org/reports/tr39}}.
-It displays the URL in Unicode when all characters belong to a single script, to a single script plus Latin, or to a the white-list of other combinations.
-Google Chrome (version 59 at the time of writing), among other things, checks Latin-look-alike Cyrillic characters in non-IDN TLDs.
-This change was introduced recently, after a proof-of-concept IDN homograph attack working on Chrome was submitted to their issue tracker\endnote{\url{https://bugs.chromium.org/p/chromium/issues/detail?id=683314}}.
-Internet Explorer and Edge (version 11 and 40 at the of writing, respectively) display the URL in Unicode if every component of the URL contains only characters from the languages configured in the operating system's \textit{Internet Options}.
-Safari (version 10 at the time of writing) has a white-list of scripts that do not contain confusable characters, and only shows the URL in Unicode for those white-listed scripts.
+Firefox (version 54) uses a mixed script detection algorithm based on the ``Moderately Restrictive'' profile defined in the \textit{Unicode Technical Standard \#39}\endnote{\url{http://www.unicode.org/reports/tr39}}.
+It displays the URL in Unicode when all characters belong to a single script, to a single script plus Latin, or to a white-list of other combinations.
+Google Chrome (version 59) performs several checks, including the search of Latin-look-alike Cyrillic characters in non-IDN TLDs.
+The check mentioned was introduced recently, after a proof-of-concept IDN homograph attack working on Chrome was submitted to their issue tracker\endnote{\url{https://bugs.chromium.org/p/chromium/issues/detail?id=683314}}.
+Internet Explorer and Edge (version 11 and 40) display the URL in Unicode if every component of the URL contains only characters from the languages configured in the operating system's \textit{Internet Options}.
+Safari (version 10) has a white-list of scripts that do not contain confusable characters, and only shows the URL in Unicode for those scripts in the white-list.
 
@@
 The first IDN ccTLD was added to DNS root zone in 2010~\cite{mac2010}.
-ICANN is aware of the potential security risk that homograph attacks pose, and limits the usage of Latin-look-alike letters.
+ICANN is aware of the potential security risk that homograph attacks pose, and limits the use of Latin-look-alike letters.
 They may reject applications for IDN ccTLDs if there already exists a TLD that looks similar to the one being petitioned for.
@@
 Several relevant studies have been conducted to describe the potential security issues with IDNs, while providing possible solutions to mitigate the surface attack of these homograph domain names.
-The first of these studies, \textit{The Homograph Attack}~\cite{gabrilovich2002}, was written by Evgeniy Gabrilovich and Alex Gontmakher in 2001, and proved the feasability of the attack.
+The first study, \textit{The Homograph Attack}, was written by Evgeniy Gabrilovich and Alex Gontmakher in 2001, and proved the feasability of the attack~\cite{gabrilovich2002}.
 
@@
 Their algorithm tries to prevent the attack by analyzing each of these URL parts.
-Each one is sent to the search engine for a spelling check, and in the cases that a spelling suggestion is returned, the URL will be marked as suspicious.
+Each one is sent to the search engine for a spell check, and in the cases that a spelling suggestion is returned, the URL will be marked as suspicious.
 By splitting the URL into these parts, this method aims to cover almost all possible cases of confusable URLs or domain names.
-However, this mechanism relies exclusively on the search engine to return spelling suggestions, and as a result, it is highly dependent on the search engine and query itself.
+However, this mechanism relies exclusively on the search engine to return spelling suggestions, resulting in its highly dependence on the search engine and query itself.
 

### 2017-06-14 docs/paper.tex
Change to present tense

@@
 This kind of attack can be used to trick users into thinking they are visiting a different (but homograph) domain name.
-Our approach to analyze its potential impact was based on clustering IDNs with their canonical counterparts in the Alexa Top 1m web sites ranking.
+Our approach to analyze its potential impact is based on clustering IDNs with their canonical counterparts in the Alexa Top 1 million web sites ranking.
 The results obtained indicate that there are more than a thousand IDN homographs among \textit{.com} domains.
@@
 The specific conditions, however, are different for each browser.
-Figure~\ref{screenshot-apple} shows a successful attack where the homograph domain name was not detected.
+Figure~\ref{screenshot-apple} shows a successful attack where the homograph domain name is not detected.
 Figure~\ref{screenshot-google} show an unsuccessful attack, where the URL is displayed in Punycode.
@@
 They proposed a more complex method based on URL components and the spell checking functionality of any search engine.
-In this method, a URL is be divided into several parts, namely, base name (the primary domain name as registered at the registrar), sub-domain (part before the primary domain, i.e., before the last identifier and TLD), path domain (sub-folder of the URL), and brand name (any popular brand name that is present in the URL).
+In this method, a URL is divided into several parts, namely, base name (the primary domain name as registered at the registrar), sub-domain (part before the primary domain, i.e., before the last identifier and TLD), path domain (sub-folder of the URL), and brand name (any popular brand name that is present in the URL).
 Their algorithm tries to prevent the attack by analyzing each of these URL parts.
@@
 
-Our approach to analyze the potential security risk of homograph IDNs was fundamentally different the ones evaluated.
-Rather than inspecting traffic or generating random homograph permutations of a string, we took a more systematic approach.
-We clustered all internationalized homograph domains using a snapshot of the \texttt{.com} domain zone.
-We then used a list of top web sites and domain registrants data to classify each homograph domain name.
+Our approach to analyze the potential security risk of homograph IDNs is fundamentally different from the ones evaluated.
+Rather than inspecting traffic or generating random homograph permutations of a string, we take a more systematic approach.
+We cluster all internationalized homograph domains using a snapshot of the \texttt{.com} domain zone.
+We then use a list of top web sites and domain registrants data to classify each homograph domain name.
 
 \section{Methodology}
-Our data collection involved two primary sources.
-The first one was a snapshot of the \texttt{.com} and \texttt{.net} domain zone, from now on referenced as \textit{.com snapshot}.
-This snapshot was provided by Verisign\endnote{\url{https://www.verisign.com/en_US/channel-resources/domain-registry-products/zone-file/index.xhtml}}, and it is dated on 2017/05/01.
+Our data collection involves two primary sources.
+The first one is a snapshot of the \texttt{.com} and \texttt{.net} domain zone, from now on referenced as \textit{.com snapshot}.
+This snapshot has been provided by Verisign\endnote{\url{https://www.verisign.com/en_US/channel-resources/domain-registry-products/zone-file/index.xhtml}}, and it is dated on 2017/05/01.
 It contains, for the most part, the name servers of all \texttt{.com} and \texttt{.net} domains.
-For the purposes of this project, only the \texttt{.com} domains were considered.
+For the purposes of this project, only the \texttt{.com} domains have been considered.
 
-The second data source was the \textit{Alexa Top 1 million sites ranking}\endnote{\url{https://www.alexa.com/topsites}}, from now on referenced as \textit{top domains snapshot}.
+The second data source is the \textit{Alexa Top 1 million sites ranking}\endnote{\url{https://www.alexa.com/topsites}}, from now on referenced as \textit{top domains snapshot}.
 It contains the most popular one million web sites (as ranked by Alexa), regardless whether they are \texttt{.com} domains or not.
@@
 \subsection{Data Processing}
-We used the \textit{.com snapshot} to obtain all the internationalized domains of the \texttt{.com} domain zone.
+We use the \textit{.com snapshot} to obtain all the internationalized domains of the \texttt{.com} domain zone.
 All IDNs are represented using Punycode, so they start with the \texttt{xn--} prefix.
-Using this information we first filtered the \textit{.com snapshot} to match only the \texttt{.com} domains that start with \texttt{xn--}.
+Using this information we first filter the \textit{.com snapshot} to match only the \texttt{.com} domains that start with \texttt{xn--}.
 Since the \textit{.com snapshot} contains name server records, a single domain may have more than one entry in the file.
-Only the domain name is relevant for this project, so the rest of the columns of the \textit{.com snapshot} were discarded.
-We sorted the domains in lexicographical order, removing duplicates in the process.
+Only the domain name is relevant for this project, so the rest of the columns of the \textit{.com snapshot} can be discarded.
+We sort the domains in lexicographical order, removing duplicates in the process.
 
-We used the \textit{top domains snapshot} as a source for the canonical (non-international) domain name of a website, based on its ranking.
-As we were only interested in non-IDNs, we discarded the ones that start with the prefix \texttt{xn--}.
-We also removed sub-domains, since we only had second level domain names in the \textit{.com snapshot}.
+We use the \textit{top domains snapshot} as a source for the canonical (non-international) domain name of a website, based on its ranking.
+As we are only interested in non-IDNs, we can discard the ones that start with the prefix \texttt{xn--}.
+We also remove sub-domains, since we only have second level domain names in the \textit{.com snapshot}.
 
@@
 The underlying assumptions behind the clustering process are that homograph attacks are more likely to target popular domains, and that the million domains from the \textit{top domains snapshot} contains most of the popular domains.
-To detect potential internationalized domain name homograph attacks, we clustered the IDNs in the \textit{.com snapshot}.
-The representative of each cluster is a homograph domain name from the \textit{top domains snapshot}, which we called canonical domain name.
-Only clusters with at least one internationalized homograph domain name were output.
+To detect potential internationalized domain name homograph attacks, we cluster the IDNs in the \textit{.com snapshot}.
+The representative of each cluster is a homograph domain name from the \textit{top domains snapshot}, which we call canonical domain name.
+Only clusters with at least one internationalized homograph domain name are output.
 
-The detection of homograph domain names was done using an algorithm to check if two strings are confusable.
+The detection of homograph domain names is done using an algorithm to check if two strings are confusable.
 This algorithm is described in the \textit{Unicode Technical Standard \#39}.
@@
 More sophisticated homographs can also be generated by using Unicode characters similar to ``/''.
-It is also worth noting that only domain names from the \texttt{.com} zone were considered, but similar studies could be done to other top-level domains following the same procedure.
+It is also worth noting that only domain names from the \texttt{.com} zone are considered, but similar studies could be done to other top-level domains following the same procedure.
 All things considered, we still think this approach is a valuable first step.
 
-Another type of clustering was also performed.
-We grouped the homograph domain names by its registrant organization, and ranked each organization by the number of homograph domain names to their name.
+Another type of clustering is also performed.
+We group the homograph domain names by its registrant organization, and rank each organization by the number of homograph domain names to their name.
 This could shed light on which registrant organizations are allowing homograph domain names, or even on which individuals and companies are doing it the most.
@@
 \subsection{Manual Classification}
-The last part of the data processing was the classification of the homograph domain names.
-This classification was done manually, to be able to differentiate between scam and unrelated websites.
-To help with the classification and speed up the process, we queried the \textit{WHOIS} records\endnote{\url{https://whois.icann.org}} of every homograph domain name.
-Some domains had expired at the time of the classification, and were subsequently deleted from the output file.
+The last part of the data processing is the classification of the homograph domain names.
+This classification is done manually, to be able to differentiate between scam and unrelated websites.
+To help with the classification and speed up the process, we query the \textit{WHOIS} records\endnote{\url{https://whois.icann.org}} of every homograph domain name.
+Some domains are expired at the time of the classification, and are subsequently deleted from the output file.
 
-The two high level categories that were defined are \textit{Canonical} and \textit{Third Party}.
-The first one, \textit{Canonical}, was employed when the domain is registered by the same organization as its canonical homograph domain name.
-The second one, \textit{Third Party}, was used when the domain is registered by a different organization than its canonical homograph domain name.
-Additionally, a more detailed classification was made:
+The two high level categories defined are \textit{Canonical} and \textit{Third Party}.
+The first one, \textit{Canonical}, is employed when the domain is registered by the same organization as its canonical homograph domain name.
+The second one, \textit{Third Party}, is used when the domain is registered by a different organization than its canonical homograph domain name.
+Additionally, a more detailed classification is made:
 \begin{itemize}
@@
 \setlength{\parsep}{0pt}
-\item \textit{Canonical - Parking}: domain was registered but it was not accessible via HTTP.
-\item \textit{Canonical - Redirect}: domain redirected (HTTP Status Code 301/307/308) to its canonical homograph domain name.
-\item \textit{Third Party - Redirect to Canonical:} domain redirected (HTTP Status Code 301/307/308) to its canonical homograph domain name.
-\item \textit{Third Party - Unrelated}: domain resolved, but the contents of the website were totally unrelated to its canonical homograph domain name.
-\item \textit{Third Party - Parking}: domain was registered, but it was not accessible via HTTP, or when accessed, a default domain parking web page was displayed.
-\item \textit{Third Party - Scam}: domain resolved, and the website displayed was a clear attempt (similar color, logos, etc.) to make users think they were visiting the canonical homograph domain name.
+\item \textit{Canonical - Parking}: domain is registered but it is not accessible via HTTP.
+\item \textit{Canonical - Redirect}: domain redirects (HTTP Status Code 301/307/308) to its canonical homograph domain name.
+\item \textit{Third Party - Redirect to Canonical:} domain redirects (HTTP Status Code 301/307/308) to its canonical homograph domain name.
+\item \textit{Third Party - Unrelated}: domain resolves, but the contents of the website are totally unrelated to its canonical homograph domain name.
+\item \textit{Third Party - Parking}: domain is registered, but it is not accessible via HTTP, or when accessed, a default domain parking web page is displayed.
+\item \textit{Third Party - Scam}: domain resolves, and the website displayed is a clear attempt (similar color, logos, etc.) to make users think they are visiting the canonical homograph domain name.
 \end{itemize}
@@
 \section{Results}
-We obtained 458731 domain names from the \textit{top domains snapshot} that belonged to the \texttt{.com} zone.
-From the \textit{.com snapshot}, we identified a total of 1044301 internationalized domains.
-However, only a low percentage of the IDNs (3.68\%) had a matching homograph canonical domain name in the \textit{top domains snapshot}.
+We obtain 458731 domain names from the \textit{top domains snapshot} that belong to the \texttt{.com} zone.
+From the \textit{.com snapshot}, we identify a total of 1044301 internationalized domains.
+However, only a low percentage of the IDNs (3.68\%) have a matching homograph canonical domain name in the \textit{top domains snapshot}.
 Even if we take into account that our homograph detection algorithm is rather limited (as described before), these results still indicate that the majority of IDNs are not being used in homograph attacks.
@@
 \section{Ethical Considerations}
-The domain information used in this project is publicly available, and was voluntarily provided by the registrants of the domains when they registered them.
+The domain information we use in this project is publicly available, and is voluntarily provided by the registrants of the domains when they register them.
 The full \texttt{.com} domain zone snapshot will not be publicly disclosed, as its access requires a paid subscription.
-The retrieval of the \textit{WHOIS} information was performed only for the homograph IDNs, which were about one thousand.
-It was performed with a significant delay between petitions (3 seconds) in order to avoid saturating the servers.
+The retrieval of the \textit{WHOIS} information is done only for the homograph IDNs, which are about one thousand.
+It is performed with a significant delay between petitions (3 seconds) in order to avoid saturating the servers.
 

### 2017-06-14 docs/paper.tex
More typos

@@
 This kind of attack can be used to trick users into thinking they are visiting a different (but homograph) domain name.
-Our approach to analyze its potential impact is based on clustering IDNs with their canonical counterparts in the Alexa Top 1 million web sites ranking.
+Our approach to analyze its potential impact is based on clustering IDNs with their canonical counterparts in the Alexa Top 1 million websites ranking.
 The results obtained indicate that there are more than a thousand IDN homographs among \textit{.com} domains.
@@
 \section{Background}
-This section summarizes different mechanisms used to defend against internationalized domain name homograph attack.
+This section summarizes different mechanisms used to defend against IDN homograph attacks.
 There are two major players trying to prevent this kind of attack, browsers and TLDs.
@@
 
-Firefox (version 54) uses a mixed script detection algorithm based on the ``Moderately Restrictive'' profile defined in the \textit{Unicode Technical Standard \#39}\endnote{\url{http://www.unicode.org/reports/tr39}}.
+Firefox (version 54) uses a mixed script detection algorithm based on the ``Moderately Restrictive'' profile defined in the \textit{Unicode Technical Standard \#39}\endnote{\label{tr39}\url{http://www.unicode.org/reports/tr39}}.
 It displays the URL in Unicode when all characters belong to a single script, to a single script plus Latin, or to a white-list of other combinations.
@@
 Other attempts to analyze the impact of homograph attacks have also been made.
-In 2009, Peter Hanay and Christopher Bolan~\cite{hannay2009} concluded that, while most modern browsers in fact have implemented useful measures to prevent internationalized domain name homograph attacks, email clients where not nearly as effective, specially when dealing with incoming emails.
+In 2009, Peter Hanay and Christopher Bolan~\cite{hannay2009} concluded that, while most modern browsers in fact have implemented useful measures to prevent IDN homograph attacks, email clients were not nearly as effective, specially when dealing with incoming emails.
 In 2010, Johnny Al Helou and Scott Tilley~\cite{al2010} argued that the introduction of ccTLDs have made this attack easier to perform again.
@@
 We cluster all internationalized homograph domains using a snapshot of the \texttt{.com} domain zone.
-We then use a list of top web sites and domain registrants data to classify each homograph domain name.
+We then use a list of top websites and domain registrants data to classify each homograph domain name.
 
@@
 The second data source is the \textit{Alexa Top 1 million sites ranking}\endnote{\url{https://www.alexa.com/topsites}}, from now on referenced as \textit{top domains snapshot}.
-It contains the most popular one million web sites (as ranked by Alexa), regardless whether they are \texttt{.com} domains or not.
+It contains the most popular one million websites (as ranked by Alexa), regardless whether they are \texttt{.com} domains or not.
 It was also retrieved on 2017/05/01.
@@
 Since the \textit{.com snapshot} contains name server records, a single domain may have more than one entry in the file.
-Only the domain name is relevant for this project, so the rest of the columns of the \textit{.com snapshot} can be discarded.
+Only the domain name is relevant to this project, so the rest of the columns of the \textit{.com snapshot} can be discarded.
 We sort the domains in lexicographical order, removing duplicates in the process.
 
-We use the \textit{top domains snapshot} as a source for the canonical (non-international) domain name of a website, based on its ranking.
+We use the \textit{top domains snapshot} as a source for the canonical (non-international) domain name of a website.
 As we are only interested in non-IDNs, we can discard the ones that start with the prefix \texttt{xn--}.
@@
 The underlying assumptions behind the clustering process are that homograph attacks are more likely to target popular domains, and that the million domains from the \textit{top domains snapshot} contains most of the popular domains.
-To detect potential internationalized domain name homograph attacks, we cluster the IDNs in the \textit{.com snapshot}.
+To detect potential IDN homograph attacks, we cluster the IDNs in the \textit{.com snapshot}.
 The representative of each cluster is a homograph domain name from the \textit{top domains snapshot}, which we call canonical domain name.
@@
 The detection of homograph domain names is done using an algorithm to check if two strings are confusable.
-This algorithm is described in the \textit{Unicode Technical Standard \#39}.
+This algorithm is described in the \textit{Unicode Technical Standard \#39}\footnotemark[\ref{tr39}].
 The approach followed has some caveats, that could be addressed in future work.
@@
 Another type of clustering is also performed.
-We group the homograph domain names by its registrant organization, and rank each organization by the number of homograph domain names to their name.
+We group the homograph domain names by its registrant organization, and rank each organization by the number of homograph domain names they have registered.
 This could shed light on which registrant organizations are allowing homograph domain names, or even on which individuals and companies are doing it the most.
@@
 The last part of the data processing is the classification of the homograph domain names.
-This classification is done manually, to be able to differentiate between scam and unrelated websites.
+This classification is done manually, to differentiate between scam and unrelated websites.
 To help with the classification and speed up the process, we query the \textit{WHOIS} records\endnote{\url{https://whois.icann.org}} of every homograph domain name.
@@
 
-Table~\ref{top-com-alexa-with-idns} shows the number of internationalized domain name homographs for the top ten \texttt{.com} domains.
+Table~\ref{top-com-alexa-with-idns} shows the number of IDN homographs for the top ten \texttt{.com} domains.
 It is worth noting that most of the homograph domains of \textit{google.com} are actually registered by Google, possibly as a defensive measure.
-Another surprising result of the homograph clustering is that 81.87\% of the groups have just one homograph internationalized domain name.
+Another surprising result of the homograph clustering is that 81.87\% of the groups have just one homograph IDN.
 This suggests that this kind of attack may not be targeted only to top websites, but rather to any domain where valuable information could be scammed from users.

### 2017-06-14 docs/paper.tex
Last check

@@
 \abstract{
-The introduction of Internationalized Domain Names (IDNs) made access the web easier to non-English speakers.
-However, it also opened up the possibility of using homograph domain names maliciously, in what has been called IDN homograph attacks.
+The introduction of Internationalized Domain Names (IDNs) made it easier for non-English speakers to access the web.
+However, it also opened up the possibility of using homograph domain names maliciously, in what is called IDN homograph attacks.
 This kind of attack can be used to trick users into thinking they are visiting a different (but homograph) domain name.
@@
 Malicious attackers could then register a domain where one of the letters is actually Cyrillic but whose representation matched a Latin one.
-Users could be linked to this newly registered malicious page, and they may not have any visual indication (at least without further interaction) that the page is not the one they think they are visiting.
+Users could be linked to this newly registered scam page, and they may not have any visual indication (at least without further interaction) that the page is not the one they think they are visiting.
 
@@
 All major browsers display the URL in Punycode instead of Unicode if certain conditions are met, to defend the user against a possible IDN homograph attack.
-The specific conditions, however, are different for each browser.
+The specific criteria, however, is different for each browser.
 Figure~\ref{screenshot-apple} shows a successful attack where the homograph domain name is not detected.
@@
 
-While these last two methods were not adopted, they have influenced other possible mitigations currently implemented in most modern browsers.
+While these last two methods were not adopted, they have influenced other defense mechanisms currently implemented in most modern browsers.
 For instance, the base name of the URL is displayed in a darker color in Google Chrome and Mozilla Firefox.
@@
 Other attempts to analyze the impact of homograph attacks have also been made.
-In 2009, Peter Hanay and Christopher Bolan~\cite{hannay2009} concluded that, while most modern browsers in fact have implemented useful measures to prevent IDN homograph attacks, email clients were not nearly as effective, specially when dealing with incoming emails.
-In 2010, Johnny Al Helou and Scott Tilley~\cite{al2010} argued that the introduction of ccTLDs have made this attack easier to perform again.
+In 2009, Peter Hanay and Christopher Bolan concluded that, while most modern browsers in fact have implemented useful measures to prevent IDN homograph attacks, email clients were not nearly as effective, specially when dealing with incoming emails~\cite{hannay2009}.
+In 2010, Johnny Al Helou and Scott Tilley argued that the introduction of ccTLDs have made this attack easier to perform again~\cite{al2010}.
 
@@
 It contains, for the most part, the name servers of all \texttt{.com} and \texttt{.net} domains.
-For the purposes of this project, only the \texttt{.com} domains have been considered.
+For the purposes of this project, only the \texttt{.com} domains are considered.
 
@@
 
-In an effort to help with the reproducibility and replicability of this project, the original data and processing code used in this project has been made available in a public repository\endnote{\url{https://github.com/jsidrach/idn-homograph-attack}}.
+In an effort to help with the reproducibility and replicability of this project, the original data and processing code used in this project is available in a public repository\endnote{\url{https://github.com/jsidrach/idn-homograph-attack}}.
 
 \subsection{Data Processing}
-We use the \textit{.com snapshot} to obtain all the internationalized domains of the \texttt{.com} domain zone.
+We use the \textit{.com snapshot} to obtain all the IDNs of the \texttt{.com} domain zone.
 All IDNs are represented using Punycode, so they start with the \texttt{xn--} prefix.
@@
 The approach followed has some caveats, that could be addressed in future work.
-For instance, it does not detect a homograph of \texttt{www.google.com}, where the first ``.'' has been replaced by a similar looking Unicode character.
+For instance, it does not detect a homograph of \texttt{www.google.com}, where the first ``.'' is replaced by a similar looking Unicode character.
 More sophisticated homographs can also be generated by using Unicode characters similar to ``/''.
@@
 The last part of the data processing is the classification of the homograph domain names.
-This classification is done manually, to differentiate between scam and unrelated websites.
+This classification is done manually, to differentiate between scams and unrelated websites.
 To help with the classification and speed up the process, we query the \textit{WHOIS} records\endnote{\url{https://whois.icann.org}} of every homograph domain name.
@@
 We obtain 458731 domain names from the \textit{top domains snapshot} that belong to the \texttt{.com} zone.
-From the \textit{.com snapshot}, we identify a total of 1044301 internationalized domains.
+From the \textit{.com snapshot}, we identify a total of 1044301 IDNs.
 However, only a low percentage of the IDNs (3.68\%) have a matching homograph canonical domain name in the \textit{top domains snapshot}.
@@
 
-\begin{table}[!ht]
+Table~\ref{top-com-alexa-with-idns} shows the number of IDN homographs for the top ten \texttt{.com} domains.
+It is worth noting that most of the homograph domains of \textit{google.com} are actually registered by Google, possibly as a defensive measure.
+Another surprising result of the homograph clustering is that 81.87\% of the groups have just one homograph IDN.
+This suggests that this kind of attack may not be targeted only to top websites, but rather to any domain where valuable information could be scammed from users.
+
+\begin{table}[!h]
 \centering
@@
 
-\begin{table}[]
+\begin{table}[!ht]
 \centering
@@
 
-Table~\ref{top-com-alexa-with-idns} shows the number of IDN homographs for the top ten \texttt{.com} domains.
-It is worth noting that most of the homograph domains of \textit{google.com} are actually registered by Google, possibly as a defensive measure.
-Another surprising result of the homograph clustering is that 81.87\% of the groups have just one homograph IDN.
-This suggests that this kind of attack may not be targeted only to top websites, but rather to any domain where valuable information could be scammed from users.
-
 The manual classification sheds some light on how these homograph IDNs are currently being used.
@@
 Browsers have to balance user experience and security.
-They need to allow users to type, navigate and see domains in their language of choice; while at the same time they should avoid misleading users into thinking they are in a legitimate domain when they are not.
+They need to allow users to type and read domain names in their language of choice; while at the same time they should avoid misleading users into thinking they are in a legitimate domain when they are not.
 
@@
 
+\clearpage
+
 \theendnotes
